---
title: "Reviews online and market dynamics"
author: "Manos Giannitselis"
date: "2024-11-28"
output: html_document
---



```{r setup-opts, echo=FALSE}
# Global knitr options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(digits = 3)
```

```{r setup-libs, warning=FALSE, message=FALSE, include=FALSE}
# ── Reproducibility seed (set once here; repeated before each bootstrap call) ──
set.seed(42)

# ── Package installation and loading ──────────────────────────────────────────
required_packages <- c(
  "readr", "dplyr", "ggplot2", "here", "corrplot",
  "knitr", "kableExtra", "psych", "data.table", "jsonlite",
  "rlang", "writexl", "purrr", "sf", "tigris",
  "progress", "ndjson", "lubridate", "haven", "labelled",
  "factoextra", "stringr", "fixest", "tidyr", "zoo",
  "naniar", "ipw", "did", "sandwich", "lmtest",
  "broom", "forcats", "scales"
)

install_missing_packages <- function(packages) {
  missing <- packages[!packages %in% installed.packages()[, "Package"]]
  if (length(missing)) install.packages(missing)
}
install_missing_packages(required_packages)
lapply(required_packages, library, character.only = TRUE)

# ── Shared constants used throughout both parts ────────────────────────────────
# Controls vector: used in trimming, PCA, and Part 2's filter(if_all(...))
controls_raw <- c(
  "pct_employed", "avg_educ", "total_pop",
  "pct_female",   "avg_age",  "pct_white", "avg_income_real"
)

# Number of PCs to retain (must be consistent throughout)
n_pcs <- 4

# Counties excluded from full_panel due to extreme hurricane/flood disruption
# (Katrina 2005 – these counties have structurally missing CBP data for 2005-07)
excluded_counties <- c(
  "Orleans County", "Jefferson County",
  "St. Bernard County", "Plaquemines County", "St. Charles County"
)
```




Checking the Academic dataset.
#businesses

```{r}
# Open a connection to the business JSON file
con <- file("yelp_academic_dataset_business.json", "r")
lines <- readLines(con, n = 2)
close(con)
sample_business <- lapply(lines, fromJSON)
print(sample_business)

```


#do the same with the other json files too

```{r}

inspect_json_file <- function(filepath, n = 100) {
  con <- file(filepath, "r")
  lines <- readLines(con, n = n)
  close(con)
  sample_data <- lapply(lines, fromJSON)
  return(sample_data)
}
sample_review   <- inspect_json_file("yelp_academic_dataset_review.json", 10)
sample_user     <- inspect_json_file("yelp_academic_dataset_user.json", 10)
sample_tip      <- inspect_json_file("yelp_academic_dataset_tip.json", 10)
sample_checkin  <- inspect_json_file("yelp_academic_dataset_checkin.json", 10)

sample_business_clean <- lapply(sample_business, function(x) {
  x$hours <- NULL
  x$attributes <- NULL
  return(x)
})

```

#Inspect the names of each json file

```{r}
names(sample_business[[1]])
names(sample_review[[1]])
names(sample_user[[1]])
names(sample_tip[[1]])
names(sample_checkin[[1]])

str(sample_business[[1]], max.level = 1)
str(sample_review[[1]], max.level = 1)
str(sample_user[[1]], max.level = 1)
str(sample_tip[[1]], max.level = 1)
str(sample_checkin[[1]], max.level = 1)


```


#Turn into data frames in order to merge the data sets

```{r}
df_review   <- bind_rows(sample_review)
df_user     <- bind_rows(sample_user)
df_business <- bind_rows(sample_business_clean)
df_tip      <- bind_rows(sample_tip)
df_checkin  <- bind_rows(sample_checkin)

```



# BUSINESS JSON 


```{r}

con <- file("yelp_academic_dataset_business.json", "r")
business_lines <- readLines(con)  # ← reads the WHOLE FILE
close(con)

all_businesses <- lapply(business_lines, fromJSON)

all_businesses_clean <- lapply(all_businesses, function(x) {
  x$hours <- NULL
  x$attributes <- NULL
  return(x)
})

df_business <- bind_rows(all_businesses_clean)

df_business <- df_business %>%
  select(business_id, name, city, state, postal_code, latitude, longitude, stars, review_count, categories)
shapefile_path <- here::here("cb_2021_us_county_500k.shp")
counties <- st_read(shapefile_path)
business_sf <- st_as_sf(df_business, coords = c("longitude", "latitude"), crs = 4326)
counties <- st_transform(counties, crs = 4326)
business_with_county <- st_join(business_sf, counties)
df_business_clean <- business_with_county %>%
  as.data.frame() %>%
  select(
    business_id,
    county_name = NAME,
    state = STATEFP,
    stars,
    review_count,
    categories
  )

saveRDS(df_business_clean, file = "df_business_clean.rds")
df_business_clean <- readRDS("df_business_clean.rds")

```




# REVIEW JSON 





```{r}

system.time({
  reviews_dt <- ndjson::stream_in("yelp_academic_dataset_review.json", cls = "dt")
})
reviews_dt[, text := NULL]         
reviews_dt[, c("funny","cool") := NULL]  

biz_ids <- df_business_clean$business_id
filtered_dt <- reviews_dt[biz_ids, on = .(business_id), nomatch = 0, 
                          .(user_id, business_id, stars, useful, date)]

fwrite(filtered_dt, "reviews_filtered.csv")        
saveRDS(filtered_dt, "reviews_filtered.rds")        


```


#load the relevant dataset in case it's needed.

```{r}
filtered_dt <- readRDS("reviews_filtered.rds")

```


# USER JSON

```{r}
con <- file("yelp_academic_dataset_user.json", "r")
user_lines <- readLines(con)
close(con)
saveRDS(user_lines, file = "user_lines_raw.rds")
parsed_users <- vector("list", length(user_lines))
for (i in seq_along(user_lines)) {
  user <- fromJSON(user_lines[i])
  
  parsed_users[[i]] <- list(
    user_id = user$user_id,
    review_count = user$review_count,
    yelping_since = user$yelping_since,
    average_stars = user$average_stars
  )
  if (i %% 50000 == 0) {
    cat("Parsed", i, "users...\n")
    saveRDS(parsed_users[1:i], file = paste0("parsed_users_checkpoint_", i, ".rds"))
  }
}

df_users <- data.table::rbindlist(parsed_users, fill = TRUE)

saveRDS(df_users, file = "df_users_clean.rds")


```


# Check if the users are correctly done

```{r}
df_users <- readRDS("df_users_clean.rds")
str(df_users)
dim(df_users)
head(df_users)

```

____________________________________________________________________________


#Merging
#First we load in case rstudio has just booted.

```{r}

df_business <- readRDS("df_business_clean.rds")
df_reviews <- readRDS("reviews_filtered.rds")
df_users <- readRDS("df_users_clean.rds")
df_merged1 <- merge(df_reviews, df_business, by = "business_id", all.x = TRUE)
df_yelp <- merge(df_merged1, df_users, by = "user_id", all.x = TRUE)

str(df_yelp)
dim(df_yelp)
head(df_yelp)


saveRDS(df_yelp, "df_yelp.rds")

df_yelp <- readRDS("df_yelp.rds")

```

____________________________________________________________________________

#Now we can start the aggregation by year and country


```{r}

df_yelp <- readRDS("df_yelp.rds")
df_yelp <- df_yelp %>%
  mutate(
    year = year(as.Date(date)),
    stars = as.numeric(stars.x),  
    log_reviews = log1p(review_count.x), 
    category_group = case_when(
      grepl("Food|Restaurant|Pizza|Diners|Breakfast", categories, ignore.case = TRUE) ~ "Food",
      grepl("Health|Medical|Yoga|Massage|Spa", categories, ignore.case = TRUE) ~ "Health",
      grepl("Shopping|Store|Retail", categories, ignore.case = TRUE) ~ "Retail",
      TRUE ~ "Other"
    )
  )


df_panel <- df_yelp %>%
  group_by(state, county_name, year, category_group) %>%
  summarise(
    avg_rating = mean(stars, na.rm = TRUE),
    avg_log_reviews = mean(log_reviews, na.rm = TRUE),
    num_reviews = n(),
    .groups = "drop"
  )


head(df_panel)
saveRDS(df_panel, "panel_county_year_category.rds")

```

```{r}

str(df_panel)
head(df_panel)
dim(df_panel)

```

#Lets explore the data a bit

#N of unique counties
```{r}
length(unique(df_panel$county_name))
```

##list of unique counties
```{r}
unique(df_panel$county_name)
```


#year range per county
```{r}
df_panel %>%
  group_by(county_name) %>%
  summarise(min_year = min(year), max_year = max(year))

```
#some had NA
```{r}
sum(is.na(df_panel$county_name))
df_panel %>% filter(is.na(county_name))
df_panel <- df_panel %>% filter(!is.na(county_name))

```

```{r}
df_panel <- df_panel %>% filter(!is.na(county_name))
dim(df_panel)
saveRDS(df_panel, "panel_county_year_category_clean.rds")
df_panel <- readRDS("panel_county_year_category_clean.rds")

#✓ ✓ ✓ 

```

_________________________________________________________________________________

# IPUMS Data
```{r}
ipums_df <- read_dta("usa_00008.dta")
saveRDS(ipums_df, "ipums_data.rds")
ipums_df <- readRDS("ipums_data.rds")
ipums_df <- ipums_df %>% select(-c(hispand))
saveRDS(ipums_df, "ipums_cleaned_ready.rds")
ipums_df <- readRDS("ipums_cleaned_ready.rds")
ipums_df <- ipums_df[ipums_df$year >= 2002, ]
saveRDS(ipums_df, "ipums_years.rds")
ipums_df <- readRDS("ipums_years.rds")
ipums_df <- ipums_df %>%
  filter(countyfip != 0) %>%
  mutate(
    sex = as.character(sex),
    marst = as.character(marst),
    race = as.character(race),
    empstat = as.character(empstat),
    age = as.numeric(as.character(age)),
    educd = as.numeric(as.character(educd)),
    inctot = as.numeric(as.character(inctot)),
    ftotinc = as.numeric(as.character(ftotinc))
  )
ipums_agg <- ipums_df %>%
  group_by(statefip, countyfip, year) %>%
  summarise(
    avg_age       = weighted.mean(age, perwt, na.rm = TRUE),
    pct_female    = weighted.mean(sex == "2", perwt, na.rm = TRUE),
    pct_white     = weighted.mean(race == "1", perwt, na.rm = TRUE),
    pct_married   = weighted.mean(marst == "1", perwt, na.rm = TRUE),
    pct_employed  = weighted.mean(empstat == "1", perwt, na.rm = TRUE),
    avg_educ      = weighted.mean(educd, perwt, na.rm = TRUE),
    avg_income    = weighted.mean(inctot, perwt, na.rm = TRUE),
    total_pop     = sum(perwt, na.rm = TRUE),
    .groups = "drop"
  )
saveRDS(ipums_agg, "ipums_aggregated_county_year.rds")
ipums_agg <- readRDS("ipums_aggregated_county_year.rds")
crosswalk <- read_csv("county_fips_master.csv") %>%
  rename(
    statefip = state,
    countyfip = county
  ) %>%
  mutate(
    statefip = as.numeric(statefip),
    countyfip = as.numeric(countyfip)
  ) %>%
  distinct(statefip, countyfip, .keep_all = TRUE)
ipums_agg <- ipums_agg %>%
  left_join(crosswalk, by = c("statefip", "countyfip")) %>%
  filter(!is.na(county_name) & !is.na(state_name))
saveRDS(ipums_agg, "ipums_agg_county.rds")
ipums_agg <- readRDS("ipums_agg_county.rds")

```

_____________________________________________________________________

#CBP — vectorised loading (replaces 18 individual read.csv calls)
```{r cbp-load}
# Build file paths from year suffix (e.g. cbp22co.txt, cbp05co.txt)
cbp_years <- 2005:2022

cbp <- purrr::map_dfr(cbp_years, function(yr) {
  suffix <- sprintf("%02d", yr %% 100)
  path   <- paste0("cbp", suffix, "co.txt")
  df     <- read.csv(path, sep = ",", stringsAsFactors = FALSE)
  # Normalise column names to lowercase so column selection is safe
  names(df) <- tolower(names(df))
  df$year    <- yr
  df[, c("fipstate", "fipscty", "year", "emp", "est", "ap", "qp1")]
})

# Anti-join check: flag any CBP rows that fail to match the crosswalk
cbp_unmatched <- anti_join(cbp, crosswalk, by = c("fipstate", "fipscty"))
message(nrow(cbp_unmatched), " CBP rows unmatched after crosswalk join")
saveRDS(cbp, "cbp.rds")
cbp <- readRDS("cbp.rds")

crosswalk <- read_csv("county_fips_master.csv") %>%
  rename(
    fipstate = state,
    fipscty = county,
    county_name = county_name
  ) %>%
  mutate(
    fipstate = as.numeric(fipstate),
    fipscty = as.numeric(fipscty)
  ) %>%
  distinct(fipstate, fipscty, county_name, .keep_all = TRUE)

cbp <- cbp %>%
  left_join(crosswalk, by = c("fipstate", "fipscty")) %>%
  rename(statefip = fipstate)

cbp_agg <- cbp %>%
  filter(!is.na(county_name)) %>%
  group_by(statefip, fipscty, year) %>%
  summarise(
    emp = sum(emp, na.rm = TRUE),
    est = sum(est, na.rm = TRUE),
    ap = sum(ap, na.rm = TRUE),
    qp1 = sum(qp1, na.rm = TRUE)
  ) %>%
  ungroup()
saveRDS(cbp_agg, "cbp_agg.rds")
cbp_agg <- readRDS("cbp_agg.rds")

```

______________________________________________________________

#exploration

```{r}
rm(
  df_business, df_panel_filtered,
  sample_business, all_businesses,
  all_businesses_clean, business_sf,
  df_panel_grouped, crosswalk_clean,
  business_lines, con, lines, rows_to_keep, selected_counties
)
gc()
ipums_agg <- readRDS("ipums_agg_county.rds")
df_panel <- readRDS("panel_county_year_category_clean.rds")
cbp_agg <- readRDS("cbp_agg_county.rds")

```

```{r}
df_panel %>%
  distinct(statefip, county_name) %>%
  arrange(statefip, county_name)
df_panel %>%
  summarise(
    unique_counties = n_distinct(county_name),
    unique_states = n_distinct(statefip),
    unique_years = n_distinct(year)
  )
df_panel %>%
  count(category_group, year) %>%
  spread(category_group, n, fill = 0)
df_panel %>%
  group_by(category_group) %>%
  summarise(total_reviews = sum(num_reviews)) %>%
  mutate(share = total_reviews / sum(total_reviews))
df_panel %>%
  group_by(year) %>%
  summarise(total_reviews = sum(num_reviews, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = total_reviews)) +
    geom_line(linewidth = 1, color = "#2C77BF") +
    labs(title = "Total Yelp Reviews per Year", y = "Number of Reviews") +
    theme_minimal()
df_panel %>%
  group_by(year, category_group) %>%
  summarise(avg_rating = mean(avg_rating, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = avg_rating, color = category_group)) +
    geom_line(linewidth = 1) +
    labs(title = "Average Rating by Business Category Over Time") +
    theme_minimal()
ggplot(df_panel, aes(x = year, y = num_reviews, group = county_name)) +
  geom_line(alpha = 0.2) +
  labs(title = "Yelp Reviews Over Time by County", y = "Number of Reviews") +
  theme_minimal()
df_panel %>%
  filter(county_name == "Pima County", year == 2020) %>%
  ggplot(aes(x = reorder(category_group, avg_rating), y = avg_rating)) +
    geom_col(fill = "orange") +
    coord_flip() +
    labs(
      title = "Average Yelp Rating by Category (Pima County, 2020)",
      x = "Category Group", y = "Average Rating"
    )
df_panel %>%
  filter(county_name == "Pima County", category_group %in% c("Food", "Health", "Retail")) %>%
  ggplot(aes(x = year, y = avg_log_reviews, color = category_group)) +
    geom_line() +
    labs(
      title = "Review Count Trends by Category in Pima County",
      x = "Year", y = "Log Review Count", color = "Category"
    )
# NOTE: yelp_data / merged_data / did_df were stale references from an earlier
# draft. Replaced with the correct objects (df_panel / yelp_ipums) that exist
# at this point in the pipeline.
df_panel %>%
  group_by(county_name) %>%
  summarise(
    total_reviews  = sum(num_reviews, na.rm = TRUE),
    avg_employment = mean(pct_employed, na.rm = TRUE)
  ) %>%
  arrange(desc(total_reviews))
df_panel %>%
  group_by(category_group) %>%
  summarise(
    mean_reviews   = mean(num_reviews, na.rm = TRUE),
    median_reviews = median(num_reviews, na.rm = TRUE),
    n = n()
  )
ggplot(df_panel, aes(x = num_reviews)) +
  geom_histogram(binwidth = 250, fill = "#2C77BF", color = "white") +
  theme_minimal() +
  labs(title = "Distribution of Review Counts")
ggplot(df_panel, aes(x = num_reviews)) +
  geom_histogram(binwidth = 100, fill = "#2C77BF", color = "white", alpha = 0.8) +
  geom_vline(aes(xintercept = mean(num_reviews, na.rm = TRUE)), color = "red", linetype = "dashed", linewidth = 1.1) +
  geom_vline(aes(xintercept = median(num_reviews, na.rm = TRUE)), color = "darkgreen", linetype = "dashed", linewidth = 1.1) +
  coord_cartesian(xlim = c(0, 3000)) +
  labs(
    title = "Distribution of Yelp Reviews per County-Year",
    x = "Number of Reviews", y = "Count of County-Year Observations"
  ) +
  theme_minimal()

```



```{r}
yelp_ipums <- readRDS("yelp_ipums.rds")
yelp_ipums %>%
  group_by(year) %>%
  summarise(
    mean_reviews = mean(num_reviews, na.rm = TRUE),
    median_reviews = median(num_reviews, na.rm = TRUE),
    n_counties = n_distinct(county_name)
  ) %>%
  ggplot(aes(x = year)) +
    geom_line(aes(y = mean_reviews), color = "blue", linewidth = 1) +
    geom_line(aes(y = median_reviews), color = "red", linetype = "dashed") +
    labs(
      title = "Mean and Median Yelp Reviews per County-Year (Merged Dataset)",
      y = "Number of Reviews", x = "Year"
    ) +
    theme_minimal()
ggplot(yelp_ipums, aes(x = num_reviews)) +
  geom_histogram(binwidth = 100, fill = "#2C77BF", color = "white", alpha = 0.8) +
  geom_vline(aes(xintercept = mean(num_reviews, na.rm = TRUE)), color = "red", linetype = "dashed", linewidth = 1.1) +
  geom_vline(aes(xintercept = median(num_reviews, na.rm = TRUE)), color = "darkgreen", linetype = "dashed", linewidth = 1.1) +
  coord_cartesian(xlim = c(0, 3000)) +
  labs(
    title = "Distribution of Yelp Reviews per County-Year",
    x = "Number of Reviews", y = "Count of County-Year Observations"
  ) +
  theme_minimal()
quantile(yelp_ipums$num_reviews, probs = seq(0, 1, 0.1), na.rm = TRUE)
percentiles <- seq(0, 1, by = 0.1)
review_quantiles <- quantile(yelp_ipums$num_reviews, probs = percentiles, na.rm = TRUE)
quantile_table <- data.frame(
  Percentile = paste0(names(review_quantiles)),
  Review_Count = as.numeric(review_quantiles)
)
print(quantile_table)
kable(quantile_table, caption = "Percentiles of Yelp Review Counts per County-Year")
yelp_ipums %>%
  group_by(year) %>%
  summarise(across(c(num_reviews, avg_rating, avg_income, pct_employed, avg_age, pct_white), mean, na.rm = TRUE))
yelp_ipums %>%
  group_by(year) %>%
  summarise(total_reviews = sum(num_reviews)) %>%
  ggplot(aes(x = year, y = total_reviews)) +
    geom_line() +
    geom_vline(xintercept = 2012, linetype = "dashed", color = "red") +
    labs(title = "Total Yelp Reviews Over Time", y = "Total Reviews")
yelp_ipums <- yelp_ipums %>%
  group_by(county_name) %>%
  arrange(year) %>%
  mutate(lag_reviews = lag(num_reviews))
cor.test(yelp_ipums$avg_income, yelp_ipums$lag_reviews, use = "complete.obs")
table(table(yelp_ipums$county_name))
yelp_ipums %>%
  group_by(county_name) %>%
  summarise(n_years = n_distinct(year)) %>%
  arrange(n_years)
hist(log(yelp_ipums$num_reviews + 1), breaks = 50)
yelp_ipums <- yelp_ipums %>%
  mutate(log_reviews = log(num_reviews + 1))
yelp_ipums %>%
  group_by(category_group) %>%
  summarise(total_reviews = sum(num_reviews), avg_income = mean(avg_income, na.rm = TRUE)) %>%
  arrange(desc(total_reviews))
yelp_ipums %>%
  group_by(year) %>%
  summarise(
    avg_reviews = mean(num_reviews, na.rm = TRUE),
    avg_income = mean(avg_income, na.rm = TRUE)
  ) %>%
  ggplot(aes(year)) +
    geom_line(aes(y = avg_reviews, color = "Average Reviews")) +
    geom_line(aes(y = avg_income / max(avg_income) * max(avg_reviews), color = "Average Income (scaled)")) +
    scale_y_continuous(
      name = "Average Reviews",
      sec.axis = sec_axis(~ . * max(yelp_ipums$avg_income, na.rm = TRUE) / max(yelp_ipums$num_reviews, na.rm = TRUE),
                          name = "Average Income")
    ) +
    theme_minimal() +
    labs(title = "Average Yelp Reviews vs Income Over Time")
yelp_ipums %>%
  group_by(year) %>%
  summarise(
    avg_rating = mean(avg_rating, na.rm = TRUE),
    employment_rate = mean(pct_employed, na.rm = TRUE)
  ) %>%
  ggplot(aes(year)) +
    geom_line(aes(y = avg_rating, color = "Average Yelp Rating")) +
    geom_line(aes(y = employment_rate * max(avg_rating), color = "Employment Rate (scaled)")) +
    scale_y_continuous(
      name = "Average Yelp Rating",
      sec.axis = sec_axis(~ . / max(yelp_ipums$avg_rating, na.rm = TRUE),
                          name = "Employment Rate")
    ) +
    theme_minimal() +
    labs(title = "Average Yelp Rating vs Employment Rate Over Time")
yelp_ipums %>%
  group_by(county_name) %>%
  summarise(
    std_reviews = sd(num_reviews, na.rm = TRUE),
    std_income = sd(avg_income, na.rm = TRUE),
    std_rating = sd(avg_rating, na.rm = TRUE)
  ) %>%
  arrange(desc(std_reviews))
install.packages("fixest", repos = "https://cran.rstudio.com/", dependencies = TRUE)
library(fixest)
fe_model <- feols(avg_income ~ num_reviews + avg_rating | county_name + year, data = yelp_ipums)
summary(fe_model)
merged_grouped <- yelp_ipums %>%
  group_by(county_name, year) %>%
  summarise(
    avg_income = mean(avg_income, na.rm = TRUE),
    avg_rating = mean(avg_rating, na.rm = TRUE),
    total_reviews = sum(num_reviews, na.rm = TRUE),
    .groups = "drop"
  )
merged_grouped <- yelp_ipums %>%
  group_by(county_name, year, category_group) %>%
  summarise(
    avg_income = mean(avg_income, na.rm = TRUE),
    avg_rating = mean(avg_rating, na.rm = TRUE),
    total_reviews = sum(num_reviews, na.rm = TRUE),
    avg_age = mean(avg_age, na.rm = TRUE),
    .groups = "drop"
  )
ggplot(merged_grouped, aes(x = year, y = avg_income, group = county_name)) +
  geom_line(alpha = 0.4) +
  labs(title = "Average Income Over Time by County")
ggplot(merged_grouped, aes(x = year, y = total_reviews, group = county_name)) +
  geom_line(alpha = 0.4) +
  labs(title = "Total Yelp Reviews Over Time by County")
yelp_ipums %>%
  group_by(county_name) %>%
  summarise(n_years = n_distinct(year)) %>%
  ggplot(aes(x = n_years)) +
    geom_histogram(binwidth = 1) +
    labs(title = "Number of Years per County in Panel", x = "Years", y = "Counties")
yelp_ipums %>%
  group_by(year) %>%
  summarise(total_reviews = sum(num_reviews, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = total_reviews)) +
    geom_line() +
    geom_vline(xintercept = 2012, linetype = "dashed", color = "red") +
    geom_smooth(method = "loess", se = FALSE, color = "blue") +
    labs(
      title = "Total Yelp Reviews Over Time",
      subtitle = "Dashed line = 2012 | LOESS smoother in blue",
      x = "Year", y = "Total Reviews"
    )
reviews_by_year <- yelp_ipums %>%
  group_by(year) %>%
  summarise(total_reviews = sum(num_reviews, na.rm = TRUE))
reviews_by_year <- reviews_by_year %>%
  mutate(post_2012 = ifelse(year >= 2012, 1, 0))
model_break <- lm(total_reviews ~ year * post_2012, data = reviews_by_year)
summary(model_break)
reviews_by_year %>%
  mutate(review_diff = c(NA, diff(total_reviews))) %>%
  ggplot(aes(x = year, y = review_diff)) +
    geom_line() +
    geom_hline(yintercept = 0, color = "red") +
    labs(
      title = "Year-to-Year Change in Yelp Reviews",
      y = "Δ Total Reviews"
    )
yelp_ipums %>%
  filter(county_name == "Berks County") %>%
  select(year, avg_log_reviews, num_reviews)
ipums_agg %>%
  filter(county_name == "Berks County") %>%
  select(year, avg_income, avg_age, avg_educ)
ipums_years <- ipums_agg %>%
  distinct(county_name, year) %>%
  mutate(source = "ipums")
yelp_years <- yelp_ipums %>%
  distinct(county_name, year) %>%
  mutate(source = "yelp")
year_overlap <- bind_rows(ipums_years, yelp_years) %>%
  group_by(county_name, year) %>%
  mutate(n_sources = n()) %>%
  filter(n_sources == 1) %>%
  ungroup()
year_overlap %>% count(source)
year_overlap %>%
  count(county_name, source) %>%
  arrange(desc(n))

```

```{r}
rm(list = c(
  "check_ipums",
  "corr_matrix",
  "missing_pairs",
  "missing_plot_data",
  "missing_summary",
  "valid_ipums",
  "valid_ipums_yelp"
))

```

```{r}
controls <- c("avg_income_real", "avg_income", "avg_age", "avg_educ", "pct_employed", "pct_female", "pct_white")
make_imp_trim <- function(df) {
  df_imp <- df %>%
    arrange(county_name, year) %>%
    group_by(county_name) %>%
    mutate(across(all_of(controls),
                  ~ na.approx(.x, year, na.rm = FALSE, rule=2) %>%
                    na.locf(fromLast = FALSE, na.rm = FALSE) %>%
                    na.locf(fromLast = TRUE,  na.rm = FALSE))) %>%
    ungroup()
  df_trim <- df_imp %>%
    filter(across(all_of(controls), ~ !is.na(.x)))
  list(imputed = df_imp, trimmed = df_trim)
}
agg_lists      <- make_imp_trim(agg_panel_cleaned)
agg_panel_imp  <- agg_lists$imputed
agg_panel_trim <- agg_lists$trimmed
sect_lists      <- make_imp_trim(sect_panel)
sect_panel_imp  <- sect_lists$imputed
sect_panel_trim <- sect_lists$trimmed
saveRDS(agg_panel_imp,    file = "agg_panel_imp.rds")
saveRDS(agg_panel_trim,   file = "agg_panel_trim.rds")
saveRDS(sect_panel_imp,   file = "sect_panel_imp.rds")
saveRDS(sect_panel_trim,  file = "sect_panel_trim.rds")
agg_panel_imp <- readRDS("agg_panel_imp.rds")
agg_panel_trim <- readRDS("agg_panel_trim.rds")
sect_panel_imp <- readRDS("sect_panel_imp.rds")
sect_panel_trim <- readRDS("sect_panel_trim.rds")
rm(list = setdiff(ls(),
                  c("agg_panel_imp", "agg_panel_trim",
                    "sect_panel_imp", "sect_panel_trim")))

```

```{r}
agg_panel_trim <- agg_panel_trim %>%
  mutate(
    recession08_09  = if_else(year %in% c(2008,2009), 1L, 0L),
    hurricane_zone  = if_else(
                        state_abbr %in% c("FL","TX","LA","NC","SC","GA","NY","NJ") &
                        year %in% c(2005,2008,2012),
                      1L, 0L
                    ),
    taxcut18        = if_else(year >= 2018, 1L, 0L),
    covid20         = if_else(year == 2020, 1L, 0L)
  )

```

```{r}
control_df <- agg_panel_trim %>%
  select(county_name, year,
         pct_employed, avg_educ, total_pop, pct_female, avg_age, pct_white, avg_income_real) %>%
  na.omit()
pca_res <- prcomp(control_df %>% select(-county_name, -year),
                  center = TRUE, scale. = TRUE)
scores <- as_tibble(pca_res$x[,1:3], rownames = "row_id") %>%
  mutate(row_id = as.integer(row_id))
scores <- bind_cols(control_df %>% select(county_name, year), scores)
agg_trim_pca <- agg_panel_trim %>%
  left_join(scores, by = c("county_name", "year"))
saveRDS(scores, file = "pca_scores.rds")
scores <- readRDS("pca_scores.rds")
saveRDS(agg_trim_pca, file = "agg_trim_pca.rds")
agg_trim_pca <- readRDS("agg_trim_pca.rds")

```

```{r}
county_var_stats <- agg_panel_imp %>%
  group_by(county_name) %>%
  summarise(
    mean_log_reviews = mean(avg_log_reviews, na.rm = TRUE),
    sd_log_reviews   = sd(avg_log_reviews,   na.rm = TRUE),
    mean_emp         = mean(emp,         na.rm = TRUE),
    sd_emp           = sd(emp,           na.rm = TRUE)
  ) %>%
  arrange(desc(sd_log_reviews))
print(county_var_stats)
county_sd_dist <- county_var_stats %>%
  summarise(
    median_sd_reviews = median(sd_log_reviews),
    min_sd_reviews    = min(sd_log_reviews),
    max_sd_reviews    = max(sd_log_reviews)
  )
print(county_sd_dist)
ggplot(agg_panel_trim, aes(x = reorder(county_name, avg_log_reviews, FUN = median),
                           y = avg_log_reviews)) +
  geom_boxplot(outlier.size = 1) +
  coord_flip() +
  labs(x = "County", y = "Log(Reviews + 1)",
       title = "Distribution of Yelp Reviews (log) by County") +
  theme_minimal()
ggplot(agg_panel_trim, aes(x = reorder(county_name, emp, FUN = median),
                           y = emp)) +
  geom_boxplot(outlier.size = 1) +
  coord_flip() +
  labs(x = "County", y = "Employment",
       title = "Distribution of Employment by County") +
  theme_minimal()
ggplot(county_var_stats, aes(x = sd_log_reviews, y = sd_emp, label = county_name)) +
  geom_point() +
  geom_text(size = 3, vjust = -0.5) +
  labs(x = "SD of Log Reviews", y = "SD of Employment",
       title = "County-level Volatility: Yelp vs Employment") +
  theme_minimal()
county_var_stats <- county_var_stats %>%
  mutate(
    cv_log_reviews = sd_log_reviews / mean_log_reviews,
    cv_emp         = sd_emp         / mean_emp
  )
head(county_var_stats %>% arrange(desc(cv_log_reviews)), 10)
county_summary_enriched <- agg_panel_trim %>%
  group_by(county_name) %>%
  summarise(
    Years             = n_distinct(year),
    `Avg Log Reviews` = mean(avg_log_reviews, na.rm = TRUE),
    `std. Log Reviews`  = sd(avg_log_reviews, na.rm = TRUE),
    `Avg Establish.`  = mean(est,            na.rm = TRUE),
    `std. Establish.`   = sd(est,            na.rm = TRUE),
    `Avg Payroll`     = mean(ap,             na.rm = TRUE),
    `std. Payroll`      = sd(ap,             na.rm = TRUE),
    `Avg Population`  = mean(total_pop,      na.rm = TRUE)
  ) %>%
  ungroup() %>%
  arrange(desc(`Avg Log Reviews`))
print(county_summary_enriched)
n_trimmed <- nrow(agg_panel_trim)
n_imputed <- nrow(agg_panel_imp)
pct_gain  <- (n_imputed - n_trimmed) / n_trimmed * 100
cat("Trimmed obs:", n_trimmed,
    " Imputed obs:", n_imputed,
    sprintf("  →  %0.1f%% more with imputation\n", pct_gain))
n_trimmed_s <- nrow(panel_full_trim)
n_imputed_s <- nrow(panel_full_imp)
pct_gain  <- (n_imputed_s - n_trimmed_s) / n_trimmed_s * 100
cat("Trimmed obs:", n_trimmed_s,
    " Imputed obs:", n_imputed_s,
    sprintf("  →  %0.1f%% more with imputation\n", pct_gain))
agg_trim_pca %>%
  distinct(county_name) %>%
  tally(name = "n_counties")
agg_trim_pca %>%
  distinct(state_abbr, county_name) %>%
  count(state_abbr, name = "n_counties") %>%
  arrange(desc(n_counties))

```



```{r}
controls <- c(
  "avg_income_real",
  "avg_age",
  "avg_educ",
  "pct_employed",
  "pct_female",
  "pct_white"
)
miss_raw <- agg_panel %>%
  group_by(year) %>%
  summarize(across(all_of(controls), ~ mean(is.na(.x))*100)) %>%
  mutate(stage="Before interpolation")
miss_imp <- agg_imp_pca_covid %>%
  group_by(year) %>%
  summarize(across(all_of(controls), ~ mean(is.na(.x))*100)) %>%
  mutate(stage="After interpolation")
miss_long <- bind_rows(miss_raw, miss_imp) %>%
  pivot_longer(cols = -c(year,stage),
               names_to  = "variable",
               values_to = "pct_missing")
ggplot(miss_long, aes(x=year, y=pct_missing, color=stage)) +
  geom_line() +
  facet_wrap(~variable, ncol=2) +
  labs(y="% of county‐years missing",
       title="Missingness in ACS Controls: Before vs. After Linear Interpolation") +
  theme_minimal()
ggsave(
  filename = "missingness_controls.pdf",
  device   = cairo_pdf,
  width    = 8,
  height   = 6,
  units    = "in"
)

```

```{r}
library(sf)
library(dplyr)
library(ggplot2)
library(stringr)
counties_sf <- st_read("cb_2021_us_county_500k.shp", quiet = TRUE)
active_fips <- panel_full %>% 
  distinct(fips) %>% 
  mutate(
    GEOID = str_pad(as.character(fips), width = 5, side = "left", pad = "0")
  ) %>% 
  pull(GEOID)
counties_sf <- counties_sf %>%
  mutate(
    active = (GEOID %in% active_fips)
  )
p <- ggplot(counties_sf) +
  geom_sf(data = filter(counties_sf, !active),
          fill = "gray90", color = NA) +
  geom_sf(data = filter(counties_sf, active),
          fill = "steelblue", color = NA) +
  coord_sf(crs = st_crs(5070)) +
  theme_void() +
  labs(
    title = "Yelp-Active U.S. Counties (N = 374)",
    subtitle = "Shaded counties had at least one Yelp review by 2022",
    caption  = "Source: CB 2021 county boundaries; Yelp business data"
  ) +
  theme(
    plot.title    = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    plot.caption  = element_text(size = 8, color = "gray35"),
    panel.background = element_rect(fill = "gray80", color = NA)
  )
print(p)
ggsave(
  "yelp_active_counties_map.pdf", 
  plot   = p,
  width  = 8, 
  height = 5, 
  units  = "in",
  device = cairo_pdf
)
ever_reviewed <- panel_full %>%
  group_by(county_name.x, fips) %>%
  summarise(ever_reviewed = any(num_reviews > 0), .groups="drop")
ever_reviewed %>% 
  summarise(
    n_ever = sum(ever_reviewed),
    total = n(),
    pct    = 100 * n_ever / total
  )

```


```{r}
counties_sf <- st_read("cb_2021_us_county_500k.shp") %>%
  st_transform(crs = 4326) %>%
  mutate(
    GEOID = as.integer(GEOID)
  )
panel_flag <- panel_full %>% 
  distinct(fips) %>% 
  mutate(in_panel = TRUE)
ever_reviewed <- panel_full %>% 
  group_by(fips) %>% 
  summarize(ever = any(num_reviews > 0), .groups="drop")
counties_sf2 <- counties_sf %>% 
  left_join(panel_flag,     by = c("GEOID" = "fips")) %>% 
  left_join(ever_reviewed,  by = c("GEOID" = "fips")) %>% 
  mutate(
    fill_group = case_when(
      is.na(in_panel)       ~ "Outside\nsample",
      in_panel & ever       ~ "≥1 Yelp review",
      in_panel & !ever      ~ "No Yelp review"
    )
  )
my_cols <- c(
  "Outside\nsample"   = "#f0f0f0",
  "No Yelp review"    = "#757575",
  "≥1 Yelp review"    = "#f39b4f"
)
p <- ggplot(counties_sf2) +
  geom_sf(aes(fill = fill_group), color = NA) +
  scale_fill_manual(values = my_cols, name = NULL) +
  coord_sf(
    xlim   = c(-130, -70),
    ylim   = c(25, 52),
    expand = FALSE
  ) +
  labs(
    title    = "Yelp-Active U.S. Counties (N = 374)",
    subtitle = "Dark-gray = in-sample but no review; orange = ≥1 review; light-gray = never in sample"
  ) +
  theme_void(base_size = 16) +
  theme(
    plot.background  = element_rect(fill = "white", color = NA),
    legend.position  = "bottom",
    plot.title       = element_text(face = "bold", size = 20),
    plot.subtitle    = element_text(size = 14),
    plot.margin      = margin(10,10,10,10)
  )
ggsave("yelp_active_map1.pdf",
       plot   = p,
       device = cairo_pdf,
       width  = 12,
       height = 7,
       dpi    = 300)

```

```{r}
datasets <- list(
  sector_trim   = sect_trim_pca_covid,
  sector_imp    = sect_imp_pca_covid,
  agg_trim      = agg_trim_pca_covid,
  agg_imp       = agg_imp_pca_covid
)
per_capita_scale <- 1e3
datasets <- map(datasets, ~ .x %>%
  mutate(
    covid_case_rate  = cases  / total_pop * per_capita_scale,
    covid_death_rate = deaths / total_pop * per_capita_scale
  )
)
vars_to_summarize <- c(
  "emp", "est", "ap", "qp1",
  "num_reviews", "avg_log_reviews","avg_rating",
  "PC1", "PC2", "PC3", "PC4"
)
summarize_df <- function(df, vars) {
  df %>%
    select(all_of(vars)) %>%
    summarise(across(
      everything(),
      list(
        mean   = ~ mean(.x, na.rm=TRUE),
        median = ~ median(.x, na.rm=TRUE),
        sd     = ~ sd(.x, na.rm=TRUE),
        min    = ~ min(.x, na.rm=TRUE),
        max    = ~ max(.x, na.rm=TRUE)
      ),
      .names = "{.col}_{.fn}"
    )) %>%
    pivot_longer(
      everything(),
      names_to  = c("variable","stat"),
      names_sep = "_"
    ) %>%
    pivot_wider(
      names_from = stat,
      values_from = value
    ) %>%
    relocate(variable)
}

walk2(
  datasets,
  names(datasets),
  ~ {
    summ <- summarize_df(.x, vars_to_summarize)
    write_csv(
      summ,
      file = paste0("summary_stats_", .y, ".csv")
    )
    cat("\n\n### Summary statistics for", .y, "\n")
    print(knitr::kable(summ, digits=2))
  }
)

```

```{r}
n_trim <- agg_trim_pca_covid %>%
  group_by(year) %>%
  summarize(n_trim = n(), .groups = "drop")
n_imp <- agg_imp_pca_covid %>%
  group_by(year) %>%
  summarize(n_imp = n(), .groups = "drop")
obs_compare <- full_join(n_trim, n_imp, by = "year")
print(obs_compare)

```

```{r}
es_est <- aggte(did_est, type = "dynamic", na.rm = TRUE)
df_es_est <- data.frame(
  event_time = es_est$egt,
  att        = es_est$att.egt,
  se         = es_est$se.egt
) %>%
  mutate(
    ci_low  = att - 1.96 * se,
    ci_high = att + 1.96 * se
  )
plot(df_es_est$event_time, df_es_est$att,
     type = "b", pch = 16, xaxt = "n",
     xlab = "Years Since Yelp Entry",
     ylab = "ATT(est)",
     main = "Event‐Study: Yelp Entry → Establishments")
axis(1, at = unique(df_es_est$event_time))
arrows(x0 = df_es_est$event_time,
       y0 = df_es_est$ci_low,
       x1 = df_es_est$event_time,
       y1 = df_es_est$ci_high,
       angle = 90, code = 3, length = 0.05)
abline(h = 0, lty = 2, col = "gray")

es_ap <- aggte(did_ap, type = "dynamic", na.rm = TRUE)
df_es_ap <- data.frame(
  event_time = es_ap$egt,
  att        = es_ap$att.egt,
  se         = es_ap$se.egt
) %>%
  mutate(
    ci_low  = att - 1.96 * se,
    ci_high = att + 1.96 * se
  )
plot(df_es_ap$event_time, df_es_ap$att,
     type = "b", pch = 16, xaxt = "n",
     xlab = "Years Since Yelp Entry",
     ylab = "ATT(ap)",
     main = "Event‐Study: Yelp Entry → Annual Payroll")
axis(1, at = unique(df_es_ap$event_time))
arrows(x0 = df_es_ap$event_time,
       y0 = df_es_ap$ci_low,
       x1 = df_es_ap$event_time,
       y1 = df_es_ap$ci_high,
       angle = 90, code = 3, length = 0.05)
abline(h = 0, lty = 2, col = "gray")

es_qp1 <- aggte(did_qp1, type = "dynamic", na.rm = TRUE)
df_es_qp1 <- data.frame(
  event_time = es_qp1$egt,
  att        = es_qp1$att.egt,
  se         = es_qp1$se.egt
) %>%
  mutate(
    ci_low  = att - 1.96 * se,
    ci_high = att + 1.96 * se
  )
plot(df_es_qp1$event_time, df_es_qp1$att,
     type = "b", pch = 16, xaxt = "n",
     xlab = "Years Since Yelp Entry",
     ylab = "ATT(qp1)",
     main = "Event‐Study: Yelp Entry → Q1 Payroll")
axis(1, at = unique(df_es_qp1$event_time))
arrows(x0 = df_es_qp1$event_time,
       y0 = df_es_qp1$ci_low,
       x1 = df_es_qp1$event_time,
       y1 = df_es_qp1$ci_high,
       angle = 90, code = 3, length = 0.05)
abline(h = 0, lty = 2, col = "gray")

```
_____________________________________________________________________________

#merged
```{r}
df_panel <- df_panel %>%
  # NOTE: Appending ' County' here, BEFORE all joins, so county_name format
  # is consistent with ipums_agg and cbp crosswalk throughout the pipeline.
  mutate(county_name = paste0(county_name, " County")) %>%
  rename(statefip = state) %>%
  mutate(statefip = as.numeric(statefip))

ipums_agg <- ipums_agg %>%
  mutate(statefip = as.numeric(statefip))

distinct(df_panel, statefip, county_name) %>% arrange(statefip, county_name)
distinct(ipums_agg, statefip, county_name) %>% arrange(statefip, county_name)

n_yelp_before <- nrow(df_panel)
yelp_ipums <- df_panel %>%
  left_join(ipums_agg, by = c("statefip", "county_name", "year"))
message("yelp_ipums: ", nrow(yelp_ipums), " rows (", n_yelp_before, " before join)")
unmatched_yelp <- anti_join(df_panel, ipums_agg, by = c("statefip", "county_name", "year"))
message(nrow(unmatched_yelp), " Yelp rows unmatched in IPUMS")

saveRDS(yelp_ipums, "yelp_ipums.rds")
yelp_ipums <- readRDS("yelp_ipums.rds")

full_panel <- yelp_ipums %>%
  left_join(cbp_agg, by = c("statefip", "county_name", "year"))

saveRDS(full_panel, "full_panel.rds")
full_panel <- readRDS("full_panel.rds")

```

```{r}
fips_lookup <- sect_panel %>%
  distinct(statefip, countyfip, county_name)

all_fips <- bind_rows(
  ipums_agg   %>% select(statefip, countyfip),
  cbp_agg     %>% rename(countyfip = fipscty) %>% select(statefip, countyfip)
) %>% distinct()

year_range <- seq(
  min(c(ipums_agg$year, cbp_agg$year), na.rm = TRUE),
  max(c(ipums_agg$year, cbp_agg$year), na.rm = TRUE)
)

panel_base <- expand_grid(all_fips, year = year_range) %>%
  left_join(ipums_agg, by = c("statefip", "countyfip", "year")) %>%
  left_join(
    cbp_agg   %>% rename(countyfip = fipscty),
    by = c("statefip", "countyfip", "year")
  ) %>%
  left_join(fips_lookup, by = c("statefip", "countyfip")) %>%
  left_join(
    sect_panel %>%
      select(statefip, countyfip, year, category_group, num_reviews, avg_log_reviews, avg_rating),
    by = c("statefip", "countyfip", "year")
  ) %>%
  mutate(
    num_reviews     = replace_na(num_reviews, 0),
    avg_log_reviews = replace_na(avg_log_reviews, 0),
    avg_rating      = replace_na(avg_rating, NA_real_)
  )

panel_full <- panel_base
saveRDS(panel_full, "full_panel.rds")
panel_full <- readRDS("full_panel.rds")

```


```{r}
full_panel <- full_panel %>%
  select(-c(fips.y, state_abbr.y, state_name.y, long_name.y, sumlev.y, region.y, division.y, crosswalk.y, region_name.y, division_name.y))

full_panel_clean <- full_panel %>%
  # excluded_counties defined in setup chunk – see rationale there
  filter(!county_name %in% excluded_counties)

saveRDS(full_panel_clean, "full_panel_clean.rds")
full_panel_clean <- readRDS("full_panel_clean.rds")

missing_demo_years_clean <- full_panel_clean %>%
  filter(is.na(avg_age) | is.na(pct_employed) | is.na(avg_income)) %>%
  distinct(county_name, year) %>%
  group_by(county_name) %>%
  summarise(n_years_missing = n()) %>%
  arrange(desc(n_years_missing))

full_panel_clean %>%
  distinct(county_name) %>%
  count()

missing_years_full_panel_clean <- full_panel_clean %>%
  filter(is.na(emp)) %>%
  group_by(county_name) %>%
  summarise(n_years_missing = n()) %>%
  arrange(desc(n_years_missing))

counties_with_missing <- missing_years_full_panel_clean %>%
  filter(n_years_missing > 0) %>%
  pull(county_name)

full_panel_clean <- full_panel_clean[, !names(full_panel_clean) %in% "missing_info"]

```

```{r}
all.equal(df_panel$county_name, yelp_ipums$county_name)
all.equal(df_panel$year, yelp_ipums$year)
yelp_ipums$year <- as.numeric(yelp_ipums$year)

```

```{r}
boxplot(yelp_ipums$num_reviews, main = "Review Count Distribution")
boxplot(yelp_ipums$avg_income,   main = "Income Distribution")
summary(scale(yelp_ipums$num_reviews))

lm_check <- lm(avg_income ~ num_reviews + avg_rating + pct_employed, data = yelp_ipums)
vif(lm_check)

plot(lm_check$fitted.values, lm_check$residuals)
abline(h = 0, col = "red")

corrplot(cor(yelp_ipums %>% select_if(is.numeric), use = "complete.obs"))

```


```{r}
ipums_df <- readRDS("ipums_df.rds")
cpi_data <- ipums_df %>%
  select(year, cpi99) %>%
  distinct()
saveRDS(cpi_data, "cpi_data.rds")
cpi_data <- readRDS("cpi_data.rds")
rm(ipums_df)

full_panel_clean <- full_panel_clean %>%
  left_join(cpi_data, by = "year") %>%
  mutate(avg_income_real = avg_income / cpi99)

sect_panel <- sect_panel %>%
  mutate(avg_income_real = avg_income / cpi99)

```

```{r}
sect_panel <- readRDS("sect_panel.rds")

agg_panel <- sect_panel %>%
  group_by(statefip, county_name, year) %>%
  summarise(
    statefip    = first(statefip),
    countyfip   = first(countyfip),
    state_abbr  = first(state_abbr.x),
    state_name  = first(state_name.x),
    long_name   = first(long_name.x),
    avg_rating      = mean(avg_rating, na.rm = TRUE),
    avg_log_reviews = mean(avg_log_reviews, na.rm = TRUE),
    num_reviews     = sum(num_reviews, na.rm = TRUE),
    across(
      c(avg_age, pct_female, pct_white, pct_married, pct_employed, avg_educ, avg_income, avg_income_real, total_pop),
      ~ mean(.x, na.rm = TRUE)
    ),
    emp = sum(emp, na.rm = TRUE),
    est = sum(est, na.rm = TRUE),
    ap  = sum(ap, na.rm = TRUE),
    qp1 = sum(qp1, na.rm = TRUE),
    .groups = "drop"
  )

saveRDS(agg_panel, "agg_panel2.rds")
agg_panel <- readRDS("agg_panel2.rds")


```


```{r}
full_panel_clean %>%
  summarise(
    mean_income   = mean(avg_income, na.rm = TRUE),
    median_income = median(avg_income, na.rm = TRUE),
    sd_income     = sd(avg_income, na.rm = TRUE),
    min_income    = min(avg_income, na.rm = TRUE),
    max_income    = max(avg_income, na.rm = TRUE),
    p25_income    = quantile(avg_income, 0.25, na.rm = TRUE),
    p75_income    = quantile(avg_income, 0.75, na.rm = TRUE)
  )

full_panel_clean %>%
  group_by(year) %>%
  summarise(mean_income = mean(avg_income_real, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = mean_income)) +
    geom_line() +
    geom_point() +
    labs(
      title = "Average Income Over Time", x = "Year", y = "Average Income"
    )

ggplot(full_panel_clean, aes(x = avg_rating, y = avg_income_real)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Avg Rating vs Avg Income", x = "Avg Yelp Rating", y = "Avg Income"
  )

corr_data <- full_panel_clean %>%
  select(avg_rating, num_reviews, avg_income_real, emp, est, ap, avg_age, avg_educ) %>%
  na.omit()
corr_matrix <- cor(corr_data)
corrplot(corr_matrix, method = "color")

```


```{r}
sect_panel <- full_panel_clean
saveRDS(sect_panel, "sect_panel.rds")
sect_panel <- readRDS("sect_panel.rds")

agg_panel <- sect_panel %>%
  group_by(county_name, year) %>%
  summarise(
    avg_rating      = mean(avg_rating, na.rm = TRUE),
    avg_log_reviews = mean(avg_log_reviews, na.rm = TRUE),
    num_reviews     = sum(num_reviews, na.rm = TRUE),
    across(
      c(avg_age, pct_female, pct_white, pct_married, pct_employed, avg_educ, avg_income, avg_income_real, total_pop),
      ~ mean(.x, na.rm = TRUE)
    ),
    emp = sum(emp, na.rm = TRUE),
    est = sum(est, na.rm = TRUE),
    ap  = sum(ap, na.rm = TRUE),
    qp1 = sum(qp1, na.rm = TRUE),
    .groups = "drop"
  )

saveRDS(agg_panel, "agg_panel.rds")
agg_panel <- readRDS("agg_panel.rds")

agg_panel %>%
  group_by(year) %>%
  summarise(n_counties = n_distinct(county_name))

agg_panel %>%
  group_by(county_name) %>%
  summarise(n_years = n_distinct(year))

ggplot(agg_panel, aes(x = year, y = avg_log_reviews, group = county_name)) +
  geom_line(alpha = 0.3) +
  labs(title = "Variation in Yelp Activity (avg_log_reviews) Across Counties")

agg_panel %>%
  group_by(county_name) %>%
  summarise(sd_treatment = sd(avg_log_reviews, na.rm = TRUE)) %>%
  arrange(desc(sd_treatment))

```

```{r}
agg_panel_imp <- readRDS("agg_imp.rds")
agg_panel_trim <- readRDS("agg_trim.rds")

agg_panel_imp %>%
  group_by(year) %>%
  summarise(total_reviews = sum(num_reviews, na.rm = TRUE)) %>%
  pivot_longer(-year, names_to = "metric", values_to = "value") %>%
  ggplot(aes(x = year, y = value, color = metric)) +
    geom_line(linewidth = 1) +
      x     = "Year", y = NULL, color = ""
    ) +
    theme_minimal()

top5 <- agg_panel_imp %>%
  filter(year == 2022) %>%
  arrange(desc(avg_log_reviews)) %>%
  slice(1:5) %>%
  pull(county_name)

agg_panel_imp %>%
  filter(county_name %in% top5) %>%
  ggplot(aes(x = year, y = avg_log_reviews, group = county_name, color = county_name)) +
    geom_line() +
    geom_point() +
    labs(
      title = "Yelp Log-Review Trends for Top-5 Active Counties",
      x     = "Year", y = "Avg Log(# Reviews + 1)"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")

agg_panel_imp %>%
  ggplot(aes(x = avg_log_reviews, y = est)) +
    geom_point(alpha = 0.3) +
    geom_smooth(method = "lm", se = TRUE) +
    labs(
      title = "Yelp Log-Review vs. Number of Establishments",
      x     = "Avg Log(# Reviews + 1)", y = "Establishments"
    ) +
    theme_minimal()

corr_data <- agg_panel %>%
  select(avg_log_reviews, num_reviews, avg_rating, emp, est, ap, avg_income_real) %>%
  na.omit()
M <- cor(corr_data)
corrplot(M, method = "color", tl.cex = 0.8, number.cex = 0.7)

```


```{r}
agg_panel_imp <- readRDS("agg_imp.rds")
agg_panel_trim <- readRDS("agg_trim.rds")
sect_imp <- readRDS("sect_imp.rds")
sect_trim <- readRDS("sect_trim.rds")
agg_panel_trim <- agg_panel_trim %>%
  mutate(
    recession08_09 = as.integer(year %in% c(2008, 2009)),
    hurricane_zone = as.integer(state_abbr %in% c("FL","TX","LA","NC","SC","GA","NY","NJ") & year %in% c(2005, 2008, 2012)),
    taxcut18       = as.integer(year >= 2018),
    covid20        = as.integer(year == 2020)
  )

```

```{r}
control_df <- agg_panel_trim %>%
  select(county_name, year, pct_employed, avg_educ, total_pop, pct_female, avg_age, pct_white, avg_income_real) %>%
  na.omit()

# FIX: store n_pcs=4 consistently (was 3 in original); name object 'pca' so
# Part 2 can reference summary(pca)$rotation without error.
pca <- prcomp(control_df %>% select(-county_name, -year), center = TRUE, scale. = TRUE)
summary(pca)
screeplot(pca, type = "lines")
print(pca$rotation[, 1:n_pcs])  # n_pcs = 4, set in setup chunk

# FIX: store all 4 PCs (was 1:3)
scores <- as_tibble(pca$x[, 1:n_pcs], rownames = "row_id") %>%
  set_names(c("row_id", paste0("PC", 1:n_pcs))) %>%
  mutate(row_id = as.integer(row_id)) %>%
  select(-row_id) %>%
  bind_cols(control_df %>% select(county_name, year), .)

agg_trim_pca <- agg_panel_trim %>%
  left_join(scores, by = c("county_name", "year"))

saveRDS(scores,       file = "pca_scores.rds")
# Save the pca object itself so Part 2 can load it without needing Part 1's env
saveRDS(pca,          file = "pca.rds")
saveRDS(agg_trim_pca, file = "agg_trim_pca.rds")
# Save controls_raw so Part 2 can load it
saveRDS(controls_raw, file = "controls_raw.rds")

pca_scores   <- readRDS("pca_scores.rds")
agg_trim_pca <- readRDS("agg_trim_pca.rds")

```


```{r}
county_var_stats <- agg_panel_imp %>%
  group_by(county_name) %>%
  summarise(
    mean_log_reviews = mean(avg_log_reviews, na.rm = TRUE),
    sd_log_reviews   = sd(avg_log_reviews, na.rm = TRUE),
    mean_emp         = mean(emp, na.rm = TRUE),
    sd_emp           = sd(emp, na.rm = TRUE)
  ) %>%
  arrange(desc(sd_log_reviews))

county_sd_dist <- county_var_stats %>%
  summarise(
    median_sd_reviews = median(sd_log_reviews),
    min_sd_reviews    = min(sd_log_reviews),
    max_sd_reviews    = max(sd_log_reviews)
  )

ggplot(agg_panel_trim, aes(
  x = reorder(county_name, avg_log_reviews, FUN = median),
  y = avg_log_reviews
)) +
  geom_boxplot(outlier.size = 1) +
  coord_flip() +
  labs(
    x     = "County", y = "Log(Reviews + 1)",
    title = "Distribution of Yelp Reviews (log) by County"
  ) +
  theme_minimal()

ggplot(agg_panel_trim, aes(
  x = reorder(county_name, emp, FUN = median),
  y = emp
)) +
  geom_boxplot(outlier.size = 1) +
  coord_flip() +
  labs(
    x     = "County", y = "Employment",
    title = "Distribution of Employment by County"
  ) +
  theme_minimal()

ggplot(county_var_stats, aes(x = sd_log_reviews, y = sd_emp, label = county_name)) +
  geom_point() +
  geom_text(size = 3, nudge_y = 0.05 * max(county_var_stats$sd_emp)) +
  labs(
    x     = "SD of Log Reviews", y = "SD of Employment",
    title = "County-level Volatility: Yelp vs Employment"
  ) +
  theme_minimal()

```


```{r}
keep <- c(
  "agg_panel_imp", "agg_panel_trim",
  "sect_panel_imp", "sect_panel_trim"
)
rm(list = setdiff(ls(), keep))
ls()

```

#treatment decision and assignment


```{r}
thresholds <- full_panel_clean %>%
  group_by(year) %>%
  summarise(threshold_70 = quantile(avg_log_reviews, probs = 0.7, na.rm = TRUE))

saveRDS(thresholds, "thresholds.rds")

full_panel_clean <- full_panel_clean %>%
  left_join(thresholds, by = "year") %>%
  mutate(treat_year = ifelse(avg_log_reviews >= threshold_70, 1, 0))

first_treatment_year <- full_panel_clean %>%
  filter(treat_year == 1) %>%
  group_by(county_name) %>%
  summarise(first_treat_year = min(year))

full_panel_clean <- full_panel_clean %>%
  left_join(first_treatment_year, by = "county_name") %>%
  mutate(D_it = ifelse(!is.na(first_treat_year) & year >= first_treat_year, 1, 0))

full_panel_clean %>%
  filter(D_it == 1) %>%
  distinct(county_name) %>%
  count()

full_panel_clean %>%
  filter(D_it == 0) %>%
  distinct(county_name) %>%
  count()

full_panel_clean %>%
  filter(!is.na(first_treat_year)) %>%
  ggplot(aes(x = first_treat_year)) +
    geom_bar() +
    labs(
      title = "Timing of First Treatment (Yelp Surge)", x = "Year", y = "Number of Counties"
    )

full_panel_clean %>%
  group_by(county_name, year) %>%
  summarise(avg_rating = mean(avg_rating, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = avg_rating, group = county_name)) +
    geom_line(alpha = 0.4) +
    labs(
      title = "Average Yelp Rating Over Time by County",
      x     = "Year", y = "Average Rating"
    )

```
#continuous

```{r}
reg_cont <- feols(
  avg_income_real ~ avg_log_reviews + pct_employed + avg_educ + total_pop | county_name + year,
  data    = agg_panel_imp,
  cluster = ~county_name
)
summary(reg_cont)

run_twfe <- function(outcome, treatment, controls, data, cluster_var = "county_name") {
  fml <- as.formula(
    paste0(
      outcome, " ~ ", treatment,
      if (length(controls)) paste0(" + ", paste(controls, collapse = " + ")) else "",
      " | county_name + year"
    )
  )
  fe <- feols(fml, data = data, cluster = cluster_var)
  summary(fe)
}

data     <- agg_panel_imp
treat_ct <- "avg_log_reviews"
controls <- c("pct_employed", "avg_educ", "total_pop", "pct_female", "avg_age")

run_twfe("emp",  treat_ct, controls, data)
run_twfe("est",  treat_ct, controls, data)
run_twfe("ap",   treat_ct, controls, data)
run_twfe("qp1",  treat_ct, controls, data)

run_twfe("emp",  "num_reviews", controls, data)
run_twfe("emp",  "avg_rating",  controls, data)

```


```{r}
reg_cont <- feols(
  avg_income_real ~ avg_log_reviews + pct_employed + avg_educ + total_pop | county_name + year,
  data    = agg_panel_trim,
  cluster = ~county_name
)
summary(reg_cont)

run_twfe <- function(outcome, treatment, controls, data, cluster_var = "county_name") {
  fml <- as.formula(
    paste0(
      outcome, " ~ ", treatment,
      if (length(controls)) paste0(" + ", paste(controls, collapse = " + ")) else "",
      " | county_name + year"
    )
  )
  fe <- feols(fml, data = data, cluster = cluster_var)
  summary(fe)
}

data     <- agg_panel_trim
treat_ct <- "avg_log_reviews"
controls <- c("pct_employed", "avg_educ", "total_pop", "pct_female", "avg_age")

run_twfe("emp",  treat_ct, controls, data)
run_twfe("est",  treat_ct, controls, data)
run_twfe("ap",   treat_ct, controls, data)
run_twfe("qp1",  treat_ct, controls, data)

library(car)
ols_controls <- lm(pct_employed ~ avg_educ + total_pop + pct_female + avg_age + pct_white, data = agg_panel_trim)
vif(ols_controls)

library(lmtest)
lm_emp <- lm(
  emp ~ avg_log_reviews + pct_employed + avg_educ + total_pop + pct_female + avg_age + factor(county_name) + factor(year),
  data = agg_panel_trim
)
bptest(lm_emp)
bptest(lm_emp, ~ fitted(lm_emp) + I(fitted(lm_emp)^2), data = agg_panel_trim, studentize = TRUE)
summary(emp_trim_results, vcov = "cluster")

```


```{r}
library(plm)
plm_emp <- plm(emp ~ avg_log_reviews + pct_employed + avg_educ + total_pop + pct_female + avg_age,
               data = agg_panel_trim,
               index = c("county_name", "year"),
               model = "within")
pbgtest(plm_emp)
pcdtest(plm_emp, test = "cd")

reg_cont_dk <- feols(
  emp ~ avg_log_reviews + pct_employed + avg_educ + total_pop + pct_female + avg_age | county_name + year,
  data     = agg_panel_trim,
  panel.id = c("county_name", "year"),
  vcov     = "DK"
)
summary(reg_cont_dk)

```


```{r}
agg_panel_trim <- agg_panel_trim %>%
  mutate(
    covid20  = as.integer(year >= 2020),
    covid21  = as.integer(year == 2021)
)

agg_pre2020 <- agg_panel_trim %>%
  filter(year < 2020)

reg_preCovid_CR <- feols(
  ap ~ avg_log_reviews + avg_educ + pct_female + avg_age | county_name + year,
  data    = agg_pre2020,
  cluster = ~county_name
)
summary(reg_preCovid_CR)

reg_preCovid_CR2 <- feols(
  emp ~ avg_log_reviews + avg_educ + total_pop + pct_female + avg_age | county_name + year,
  data = agg_pre2020,
  vcov = ~county_name + year
)
summary(reg_preCovid_CR2)

```


```{r}
agg_panel_lag <- agg_panel_trim %>%
  arrange(county_name, year) %>%
  group_by(county_name) %>%
  mutate(lag_avg_log_reviews = lag(avg_log_reviews)) %>%
  ungroup()

reg_lagged <- feols(
  est ~ lag_avg_log_reviews + pct_employed + avg_educ + total_pop + pct_female + avg_age | county_name + year,
  data    = agg_panel_lag,
  cluster = ~county_name + year
)
summary(reg_lagged)

```

```{r}
thresholds <- agg_panel_trim %>%
  group_by(year) %>%
  summarise(thresh75 = quantile(avg_log_reviews, .75, na.rm = TRUE))

agg_bin <- agg_panel_trim %>%
  left_join(thresholds, by = "year") %>%
  mutate(treated = if_else(avg_log_reviews > thresh75, 1L, 0L))

did_mod <- feols(emp ~ i(treated, year, ref = 0) | county_name + year, cluster = ~county_name, data = agg_bin)
etable(did_mod)

```

```{r}
feols(est ~ avg_log_reviews + pct_employed + avg_educ + total_pop + pct_female + avg_age | year, data = agg_panel_trim, cluster = ~county_name)
feols(est ~ avg_log_reviews + pct_employed + avg_educ + total_pop + pct_female + avg_age | county_name + year, data = agg_panel_trim, cluster = ~county_name)

```

```{r}
thr75 <- quantile(agg_panel_trim$avg_log_reviews, .75, na.rm = TRUE)

first_treat <- agg_panel_trim %>%
  group_by(county_name) %>%
  summarise(first_year = min(year[avg_log_reviews > thr75], na.rm = TRUE))

agg_cont <- agg_panel_trim %>%
  left_join(first_treat, by = "county_name") %>%
  mutate(
    post       = as.integer(year >= first_year),
    intensity  = avg_log_reviews,
    cont_treat = post * intensity
  )

reg_cont_did <- feols(
  est ~ cont_treat + intensity + post + pct_employed + avg_educ + total_pop + pct_female + avg_age | county_name + year,
  cluster = ~county_name,
  data    = agg_cont
)
summary(reg_cont_did)

thr75 <- quantile(sect_panel_trim$avg_log_reviews, .75, na.rm = TRUE)

first_treat <- sect_panel_trim %>%
  group_by(county_name) %>%
  summarise(first_year = min(year[avg_log_reviews > thr75], na.rm = TRUE))

agg_cont <- sect_panel_trim %>%
  left_join(first_treat, by = "county_name") %>%
  mutate(
    post       = as.integer(year >= first_year),
    intensity  = avg_log_reviews,
    cont_treat = post * intensity
  )

reg_cont_did <- feols(
  est ~ cont_treat + intensity + post + pct_employed + avg_educ + total_pop + pct_female + avg_age | county_name + year,
  cluster = ~county_name,
  data    = agg_cont
)
summary(reg_cont_did)

l <- NULL
sect_thresh <- sect_panel_trim %>%
  group_by(category_group, year) %>%
  summarise(thresh75 = quantile(avg_log_reviews, .75, na.rm = TRUE), .groups = "drop")

sect_did <- sect_panel_trim %>%
  left_join(sect_thresh, by = c("category_group", "year")) %>%
  group_by(category_group, county_name) %>%
  mutate(first_year = min(year[avg_log_reviews > thresh75], na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    post       = as.integer(year >= first_year),
    intensity  = pmax(avg_log_reviews - thresh75, 0),
    cont_treat = post * intensity
  )

results_by_cat <- lapply(unique(sect_did$category_group), function(cat) {
  dat <- filter(sect_did, category_group == cat)
  feols(emp ~ cont_treat + pct_employed + avg_educ + total_pop + pct_female + avg_age | county_name + year, cluster = ~county_name, data = dat)
})
names(results_by_cat) <- unique(sect_did$category_group)
etable(results_by_cat)

```


```{r}
reg_preCovid_CR <- feols(
  est ~ avg_log_reviews + avg_educ + pct_female + avg_age + pct_employed + total_pop | year,
  data    = agg_pre2020,
  cluster = ~county_name
)
summary(reg_preCovid_CR)

reg_preCovid_CR <- feols(
  est ~ avg_log_reviews + avg_educ + pct_female + avg_age + pct_employed | county_name + year,
  data    = agg_pre2020,
  cluster = ~county_name
)
summary(reg_preCovid_CR)

```


```{r}
agg_trim_pca <- readRDS("agg_trim_pca.rds")
# FIX: use all 4 PCs (was only 3)
controls_pca <- paste0("PC", 1:n_pcs)
run_twf_pca <- function(outcome, treat, controls, data, cluster_var = "county_name") {
  fml <- as.formula(
    paste0(outcome, " ~ ", treat, " + ", paste(controls, collapse = " + "), " | county_name + year")
  )
  feols(fml, data = data, cluster = cluster_var)
}

mod_emp  <- run_twf_pca("emp", "avg_log_reviews", controls_pca, agg_trim_pca)
mod_est  <- run_twf_pca("est", "avg_log_reviews", controls_pca, agg_trim_pca)
mod_ap   <- run_twf_pca("ap",  "avg_log_reviews", controls_pca, agg_trim_pca)
mod_qp1  <- run_twf_pca("qp1", "avg_log_reviews", controls_pca, agg_trim_pca)

summary(mod_emp)
summary(mod_est)
summary(mod_ap)
summary(mod_qp1)
etable(mod_emp, mod_est, mod_ap, mod_qp1, tex = FALSE, digits = 3, title = "TWFE with PCA Controls")

```


```{r}
df <- agg_trim_pca
thr75 <- quantile(df$avg_log_reviews, 0.75, na.rm = TRUE)

first_treat <- df %>%
  group_by(county_name) %>%
  summarise(first_year = min(year[avg_log_reviews > thr75], na.rm = TRUE), .groups = "drop")

did_df <- df %>%
  left_join(first_treat, by = "county_name") %>%
  mutate(
    treated    = as.integer(!is.na(first_year)),
    post       = as.integer(year >= first_year),
    did_bin    = treated * post,
    intensity  = avg_log_reviews,
    did_cont   = intensity * post
  )

# FIX: use PC4 as well (was only PC1-PC3)
controls <- c("PC1", "PC2", "PC3", "PC4", "recession08_09", "hurricane_zone", "taxcut18", "covid20")
base_rhs <- paste0("did_bin + ", paste(controls, collapse = " + "))

set.seed(42)  # reproducibility
did_emp <- feols(as.formula(paste0("emp ~ ", base_rhs)), data = did_df, fixef = c("county_name", "year"), cluster = "county_name")
did_est <- feols(as.formula(paste0("est ~ ", base_rhs)), data = did_df, fixef = c("county_name", "year"), cluster = "county_name")
did_ap  <- feols(as.formula(paste0("ap  ~ ", base_rhs)), data = did_df, fixef = c("county_name", "year"), cluster = "county_name")
did_qp1 <- feols(as.formula(paste0("qp1 ~ ", base_rhs)), data = did_df, fixef = c("county_name", "year"), cluster = "county_name")

etable(
  did_emp, did_est, did_ap, did_qp1,
  se   = "cluster",
  dict = c(
    did_bin        = "Treated × Post",
    PC1            = "Demographic factor 1",
    PC2            = "Demographic factor 2",
    PC3            = "Demographic factor 3",
    recession08_09 = "2008–09 Recession",
    hurricane_zone = "Coastal hurricane zone",
    taxcut18       = "Tax cuts from 2018",
    covid20        = "COVID-20 Dummy"
  ),
  title = "Staggered DiD: Binary Yelp Treatment → County Outcomes"
)

```

```{r}
first_intro <- agg_trim_pca %>%
  group_by(county_name) %>%
  summarise(first_review = min(year[num_reviews > 0], na.rm = TRUE), .groups = "drop")

did_df <- agg_trim_pca %>%
  left_join(first_intro, by = "county_name") %>%
  mutate(
    post_intro = as.integer(year >= first_review),
    did_cont   = avg_log_reviews * post_intro
  )

controls <- c("PC1", "PC2", "PC3", "PC4")
outcome  <- "est"

iv_est <- feols(
  as.formula(paste0(
    outcome, " ~ iv(did_cont ~ post_intro) + ", paste(controls, collapse = " + ")
  )),
  data    = did_df,
  fixef   = c("county_name", "year"),
  cluster = ~county_name
)
summary(iv_est)

```

```{r}
mismatches <- anti_join(
  sect_imp_pca %>% select(county_name, state_name, year) %>% distinct(),
  covid_cy   %>% select(county_name, state_name, year) %>% distinct(),
  by = c("county_name", "state_name", "year")
)
nrow(mismatches)

```

```{r}
df_base <- read.csv("us-counties-2020.csv", stringsAsFactors = FALSE)
path    <- normalizePath("us-counties-2020.csv", winslash = "/", mustWork = TRUE)
df_base2 <- read.csv(path, stringsAsFactors = FALSE)
saveRDS(df_base, "covid_raw.rds")
covid_raw <- readRDS("covid_raw.rds")

covid_cy <- covid_raw %>%
  mutate(year = year(date)) %>%
  group_by(fips, county, state, year) %>%
  summarise(
    covid_cases  = sum(cases, na.rm = TRUE),
    covid_deaths = sum(deaths, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  rename(county_name = county, state_name = state)

saveRDS(covid_cy, "covid_cy.rds")
covid_cy <- readRDS("covid_cy.rds")
covid_cy <- covid_cy %>%
  group_by(county, state, year) %>%
  summarise(covid_cases = sum(covid_cases, na.rm = TRUE), covid_deaths = sum(covid_deaths, na.rm = TRUE), .groups = "drop")

sect_imp_covid  <- sect_imp %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))
sect_trim_pca_covid <- sect_trim_pca %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))
agg_imp_pca_covid   <- agg_imp_pca   %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))
agg_trim_pca_covid  <- agg_trim_pca  %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))

saveRDS(sect_imp_covid, "sect_imp_covid.rds")
saveRDS(sect_trim_pca_covid, "sect_trim_pca_covid.rds")
saveRDS(agg_imp_pca_covid, "agg_imp_pca_covid.rds")
saveRDS(agg_trim_pca_covid, "agg_trim_pca_covid.rds")

covid_cy_fixed <- covid_cy %>%
  mutate(
    county_name = paste(county_name, "County"),
    state_name  = str_to_title(state_name)
  )

sect_imp_pca_covid  <- sect_imp_pca_covid  %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))
sect_trim_pca_covid <- sect_trim_pca_covid %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))
agg_imp_pca_covid   <- agg_imp_pca_covid   %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))
agg_trim_pca_covid  <- agg_trim_pca_covid  %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))

add_covid_rates <- function(df) {
  df %>%
    mutate(
      covid_case_rate  = if_else(total_pop > 0, covid_cases / total_pop * 1e5, NA_real_),
      covid_death_rate = if_else(total_pop > 0, covid_deaths / total_pop * 1e5, NA_real_)
    )
}

agg_trim_pca_covid  <- add_covid_rates(agg_trim_pca_covid)
agg_imp_pca_covid   <- add_covid_rates(agg_imp_pca_covid)
sect_trim_pca_covid <- add_covid_rates(sect_trim_pca_covid)
sect_imp_pca_covid  <- add_covid_rates(sect_imp_pca_covid)

agg_trim_pca_covid    <- agg_trim_pca_covid    %>% select(-covid_case_rate, -covid_death_rate)
agg_imp_pca_covid     <- agg_imp_pca_covid     %>% select(-covid_case_rate, -covid_death_rate)
sect_trim_pca_covid   <- sect_trim_pca_covid   %>% select(-covid_case_rate, -covid_death_rate)
sect_imp_pca_covid    <- sect_imp_pca_covid    %>% select(-covid_case_rate, -covid_death_rate)

```


```{r}
df_base <- read.csv("us-counties-2020.csv", stringsAsFactors = FALSE)
path    <- normalizePath("us-counties-2020.csv", winslash = "/", mustWork = TRUE)
df_base2 <- read.csv(path, stringsAsFactors = FALSE)
saveRDS(df_base, "covid_raw.rds")
covid_raw <- readRDS("covid_raw.rds")

covid_cy <- covid_raw %>%
  mutate(year = year(date)) %>%
  group_by(fips, county, state, year) %>%
  summarise(
    covid_cases  = sum(cases, na.rm = TRUE),
    covid_deaths = sum(deaths, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  rename(county_name = county, state_name = state)

saveRDS(covid_cy, "covid_cy.rds")
covid_cy <- readRDS("covid_cy.rds")
covid_cy <- covid_cy %>%
  group_by(county, state, year) %>%
  summarise(covid_cases = sum(covid_cases, na.rm = TRUE), covid_deaths = sum(covid_deaths, na.rm = TRUE), .groups = "drop")

sect_imp_covid  <- sect_imp %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))
sect_trim_pca_covid <- sect_trim_pca %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))
agg_imp_pca_covid   <- agg_imp_pca   %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))
agg_trim_pca_covid  <- agg_trim_pca  %>% left_join(covid_cy, by = c("county_name", "state_name", "year"))

saveRDS(sect_imp_covid, "sect_imp_covid.rds")
saveRDS(sect_trim_pca_covid, "sect_trim_pca_covid.rds")
saveRDS(agg_imp_pca_covid, "agg_imp_pca_covid.rds")
saveRDS(agg_trim_pca_covid, "agg_trim_pca_covid.rds")

covid_cy_fixed <- covid_cy %>%
  mutate(
    county_name = paste(county_name, "County"),
    state_name  = str_to_title(state_name)
  )

sect_imp_pca_covid  <- sect_imp_pca_covid  %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))
sect_trim_pca_covid <- sect_trim_pca_covid %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))
agg_imp_pca_covid   <- agg_imp_pca_covid   %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))
agg_trim_pca_covid  <- agg_trim_pca_covid  %>% left_join(covid_cy_fixed, by = c("county_name", "state_name", "year"))

add_covid_rates <- function(df) {
  df %>%
    mutate(
      covid_case_rate  = if_else(total_pop > 0, covid_cases / total_pop * 1e5, NA_real_),
      covid_death_rate = if_else(total_pop > 0, covid_deaths / total_pop * 1e5, NA_real_)
    )
}

agg_trim_pca_covid  <- add_covid_rates(agg_trim_pca_covid)
agg_imp_pca_covid   <- add_covid_rates(agg_imp_pca_covid)
sect_trim_pca_covid <- add_covid_rates(sect_trim_pca_covid)
sect_imp_pca_covid  <- add_covid_rates(sect_imp_pca_covid)

agg_trim_pca_covid    <- agg_trim_pca_covid    %>% select(-covid_case_rate, -covid_death_rate)
agg_imp_pca_covid     <- agg_imp_pca_covid     %>% select(-covid_case_rate, -covid_death_rate)
sect_trim_pca_covid   <- sect_trim_pca_covid   %>% select(-covid_case_rate, -covid_death_rate)
sect_imp_pca_covid    <- sect_imp_pca_covid    %>% select(-covid_case_rate, -covid_death_rate)

```



```{r}
tt_emp <- agg_trim_pca_covid %>%
  filter(post_intro %in% c(0,1)) %>%
  do(tidy(t.test(emp ~ post_intro, data = .))) %>%
  transmute(
    outcome   = "Employment",
    mean_pre  = estimate1,
    mean_post = estimate2,
    diff      = estimate2 - estimate1,
    t_stat    = statistic,
    p_value   = p.value
  )

tt_est <- agg_trim_pca_covid %>%
  filter(post_intro %in% c(0,1)) %>%
  do(tidy(t.test(est ~ post_intro, data = .))) %>%
  transmute(
    outcome   = "Establishments",
    mean_pre  = estimate1,
    mean_post = estimate2,
    diff      = estimate2 - estimate1,
    t_stat    = statistic,
    p_value   = p.value
  )

tt_ap <- agg_trim_pca_covid %>%
  filter(post_intro %in% c(0,1)) %>%
  do(tidy(t.test(ap ~ post_intro, data = .))) %>%
  transmute(
    outcome   = "Average payroll",
    mean_pre  = estimate1,
    mean_post = estimate2,
    diff      = estimate2 - estimate1,
    t_stat    = statistic,
    p_value   = p.value
  )

tt_qp1 <- agg_trim_pca_covid %>%
  filter(post_intro %in% c(0,1)) %>%
  do(tidy(t.test(qp1 ~ post_intro, data = .))) %>%
  transmute(
    outcome   = "Q1 payroll",
    mean_pre  = estimate1,
    mean_post = estimate2,
    diff      = estimate2 - estimate1,
    t_stat    = statistic,
    p_value   = p.value
  )

tt_all <- bind_rows(tt_emp, tt_est, tt_ap, tt_qp1)

kable(
  tt_all,
  digits  = c(0, 1, 1, 1, 2, 3),
  caption = "Pre/Post‐Yelp Introduction Mean Comparisons"
)

```


```{r}
agg_trim_pca_covid %>%
  filter(year <= 2022) %>%
  group_by(year) %>%
  summarise(n_counties = sum(num_reviews > 0, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = n_counties)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    scale_x_continuous(
      limits = c(2005, 2022),
      breaks = seq(2005, 2022, by = 1)
    ) +
    scale_y_continuous(
      limits = c(0, 50),
      breaks = seq(0, 30, by = 50),
      expand = c(0, 0)
    ) +
    labs(
      title = "Diffusion of Yelp Reviews Across U.S. Counties (2005–2022)",
      x     = "Year",
      y     = "Counties with ≥1 Yelp Review"
    ) +
    theme_minimal() +
    theme(
      axis.text.x    = element_text(angle = 45, hjust = 1),
      panel.grid.minor = element_blank()
    )

```

```{r}
reviews_by_year <- sect_imp_pca_covid %>%
  group_by(year) %>%
  summarise(total_reviews = sum(num_reviews, na.rm = TRUE)) %>%
  ungroup()

ggplot(reviews_by_year, aes(x = year, y = total_reviews)) +
  geom_line(color = "darkgreen", linewidth = 1) +
  geom_point(color = "darkgreen", size = 2) +
  scale_y_continuous(labels = scales::comma_format()) +
  scale_x_continuous(breaks = seq(min(reviews_by_year$year), max(reviews_by_year$year), by = 1)) +
  labs(
    title = "Total Yelp Reviews in Our Sectoral Panel, by Year",
    x     = "Year",
    y     = "Total Number of Reviews (all sectors)"
  ) +
  theme_bw() +
  theme(
    plot.title   = element_text(hjust = 0.5),
    axis.text.x  = element_text(angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8))
  )

ggsave(
  filename = "total_reviews_over_time.pdf",
  width    = 6,
  height   = 4,
  device   = "pdf"
)

```

```{r}
sect_imp_pca_covid %>%
  filter(!is.na(category_group)) %>%
  ggplot(aes(x = category_group, y = num_reviews)) +
    geom_boxplot(fill = "lightblue", outlier.size = 1, width = 0.6) +
    scale_y_continuous(
      trans  = "log10",
      breaks = c(1, 10, 100, 1000, 10000),
      labels = scales::comma_format()
    ) +
    labs(
      title = "Distribution of Yelp Review Counts, by Sector",
      x     = "Yelp Sector",
      y     = "Number of Reviews (log scale)"
    ) +
    theme_bw() +
    theme(
      plot.title   = element_text(hjust = 0.5),
      axis.title.x = element_text(margin = margin(t = 8)),
      axis.title.y = element_text(margin = margin(r = 8))
    )

ggsave(
  filename = "boxplot_reviews_by_sector.pdf",
  width    = 6,
  height   = 4,
  device   = "pdf"
)

```

```{r}
overall_reviews_summary <- sect_imp_pca_covid %>%
  filter(!is.na(category_group)) %>%
  summarise(
    n_obs         = n(),
    mean_reviews  = mean(num_reviews, na.rm = TRUE),
    median_reviews= median(num_reviews, na.rm = TRUE),
    sd_reviews    = sd(num_reviews, na.rm = TRUE),
    min_reviews   = min(num_reviews, na.rm = TRUE),
    max_reviews   = max(num_reviews, na.rm = TRUE),
    mean_rating   = mean(avg_rating, na.rm = TRUE),
    median_rating = median(avg_rating, na.rm = TRUE),
    sd_rating     = sd(avg_rating, na.rm = TRUE),
    min_rating    = min(avg_rating, na.rm = TRUE),
    max_rating    = max(avg_rating, na.rm = TRUE)
  )

kable(
  overall_reviews_summary,
  format   = "latex",
  booktabs = TRUE,
  caption  = "Overall Summary of Yelp Statistics (All Sectors Pooled)"
)

write.table(
  overall_reviews_summary,
  file      = "overall_reviews_summary.tsv",
  sep       = "\t",
  row.names = FALSE,
  quote     = FALSE
)

```

```{r}
by_sector_reviews_summary <- sect_imp_pca_covid %>%
  filter(!is.na(category_group)) %>%
  group_by(category_group) %>%
  summarise(
    n_obs          = n(),
    mean_reviews   = mean(num_reviews, na.rm = TRUE),
    median_reviews = median(num_reviews, na.rm = TRUE),
    sd_reviews     = sd(num_reviews, na.rm = TRUE),
    min_reviews    = min(num_reviews, na.rm = TRUE),
    max_reviews    = max(num_reviews, na.rm = TRUE),
    mean_rating    = mean(avg_rating, na.rm = TRUE),
    median_rating  = median(avg_rating, na.rm = TRUE),
    sd_rating      = sd(avg_rating, na.rm = TRUE),
    min_rating     = min(avg_rating, na.rm = TRUE),
    max_rating     = max(avg_rating, na.rm = TRUE)
  ) %>%
  ungroup()

kable(
  by_sector_reviews_summary,
  format   = "latex",
  booktabs = TRUE,
  digits   = 2,
  caption  = "Yelp Summary by Sector"
)

write.csv(
  by_sector_reviews_summary,
  file      = "by_sector_reviews_summary.csv",
  row.names = FALSE
)

```

```{r}
reviews_per_business <- df_yelp %>%
  group_by(business_id) %>%
  summarise(total_reviews = n()) %>%
  ungroup()

business_summary <- reviews_per_business %>%
  summarise(
    n_businesses        = n(),
    mean_per_business   = mean(total_reviews),
    median_per_business = median(total_reviews),
    sd_per_business     = sd(total_reviews),
    min_per_business    = min(total_reviews),
    max_per_business    = max(total_reviews)
  )

business_summary

kable(
  business_summary,
  format   = "latex",
  booktabs = TRUE,
  digits   = 1,
  caption  = "Distribution of Yelp Reviews per Business (All Time)"
)

latex_overall <- kable(
  overall_reviews_summary,
  format   = "latex",
  booktabs = TRUE,
  digits   = 2,
  caption  = "Overall Summary of Yelp Statistics (All Sectors)"
)

latex_by_sector <- kable(
  by_sector_reviews_summary,
  format   = "latex",
  booktabs = TRUE,
  digits   = 2,
  caption  = "Yelp Summary by Sector"
)

cat(latex_overall, file = "overall_reviews_summary.tex", sep = "\n")
cat(latex_by_sector, file = "by_sector_reviews_summary.tex", sep = "\n")

```

```{r}
df_yelp <- df_yelp %>%
  mutate(review_date = as.Date(date)) %>%
  mutate(review_year = as.integer(format(review_date, "%Y")))

reviews_by_year <- df_yelp %>%
  count(review_year, name = "n_reviews") %>%
  filter(review_year >= 2005, review_year <= 2022)

ggplot(reviews_by_year, aes(x = review_year, y = n_reviews)) +
  geom_line(linewidth = 1, color = "steelblue") +
  geom_point(size = 2, color = "steelblue") +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Total Yelp Reviews Submitted Each Year (2005–2022)",
    x     = "Year",
    y     = "Number of Reviews"
  ) +
  theme_bw() +
  theme(
    plot.title   = element_text(hjust = 0.5, size = 14),
    axis.title.x = element_text(margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8))
  )

rating_counts <- df_yelp %>%
  count(stars.x, name = "n_reviews") %>%
  arrange(stars.x)

ggplot(rating_counts, aes(x = factor(stars.x), y = n_reviews)) +
  geom_col(fill = "tomato") +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Overall Distribution of Star Ratings (All Yelp Reviews)",
    x     = "Star Rating",
    y     = "Number of Reviews"
  ) +
  theme_bw() +
  theme(
    plot.title   = element_text(hjust = 0.5, size = 14),
    axis.title.y = element_text(margin = margin(r = 8))
  )

p_ratings <- ggplot(rating_counts, aes(x = factor(stars.x), y = n_reviews)) +
  geom_col(fill = "tomato") +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Overall Distribution of Star Ratings (All Yelp Reviews)",
    x     = "Star Rating",
    y     = "Number of Reviews"
  ) +
  theme_bw() +
  theme(
    plot.title   = element_text(hjust = 0.5, size = 14),
    axis.title.y = element_text(margin = margin(r = 8))
  )

print(p_ratings)
ggsave(
  filename = "star_rating_distribution.pdf",
  plot     = p_ratings,
  width    = 6,
  height   = 4,
  dpi      = 300
)

```

```{r}
county_rating_summary <- df_yelp %>%
  group_by(county_name) %>%
  summarise(
    n_reviews       = n(),
    avg_star_rating = mean(average_stars, na.rm = TRUE),
    median_star     = median(average_stars, na.rm = TRUE)
  ) %>%
  arrange(desc(n_reviews))

latex_county_tbl <- kable(
  county_rating_summary,
  format   = "latex",
  booktabs = TRUE,
  caption  = "Top 6 Counties by Yelp Review Volume"
)
cat(latex_county_tbl)

head(county_rating_summary, 6)
print(county_rating_summary)

ggplot(county_rating_summary, aes(x = n_reviews, y = avg_star_rating)) +
  geom_point(color = "darkgreen", alpha = 0.5) +
  scale_x_log10(labels = comma) +
  labs(
    title = "County Level Average Yelp Star Rating vs. Review Volume",
    x     = "Total Number of Reviews (log scale)",
    y     = "Mean Star Rating"
  ) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 14))

pdf("county_rating_scatter.pdf", width = 6, height = 4)
ggplot(county_rating_summary, aes(x = n_reviews, y = avg_star_rating)) +
  geom_point(color = "darkgreen", alpha = 0.5) +
  scale_x_log10(labels = comma) +
  labs(
    title = "County Level Average Yelp Star Rating vs. Review Volume",
    x     = "Total Number of Reviews (log scale)",
    y     = "Mean Star Rating"
  ) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 14))
dev.off()

```

```{r}
es_est   <- aggte(did_est,  type = "dynamic", na.rm = TRUE)
es_ap    <- aggte(did_ap,   type = "dynamic", na.rm = TRUE)
es_qp1   <- aggte(did_qp1,  type = "dynamic", na.rm = TRUE)
es_emp   <- aggte(did_mod3, type = "dynamic", na.rm = TRUE)

df_es_est <- data.frame(
  event_time = es_est$egt,
  att        = es_est$att.egt,
  se         = es_est$se.egt
) %>%
  mutate(
    ci_lo       = att - 1.96 * se,
    ci_hi       = att + 1.96 * se,
    significant = (ci_lo > 0) | (ci_hi < 0)
  )

df_es_ap <- data.frame(
  event_time = es_ap$egt,
  att        = es_ap$att.egt,
  se         = es_ap$se.egt
) %>%
  mutate(
    ci_lo       = att - 1.96 * se,
    ci_hi       = att + 1.96 * se,
    significant = (ci_lo > 0) | (ci_hi < 0)
  )

df_es_qp1 <- data.frame(
  event_time = es_qp1$egt,
  att        = es_qp1$att.egt,
  se         = es_qp1$se.egt
) %>%
  mutate(
    ci_lo       = att - 1.96 * se,
    ci_hi       = att + 1.96 * se,
    significant = (ci_lo > 0) | (ci_hi < 0)
  )

```


```{r}
p_treated <- mean(df_panel$post_intro, na.rm = TRUE)
p_control <- 1 - p_treated

df_panel <- df_panel %>%
  mutate(ps_hat = predict(ps_mod, newdata = ., type = "response")) %>%
  mutate(
    ipw_wt = if_else(
      post_intro == 1L,
      p_treated / ps_hat,
      p_control / (1 - ps_hat)
    )
  )

library(broom)
library(dplyr)
library(knitr)

outcomes   <- c("emp", "est", "ap", "qp1")
ipw_models <- vector("list", length(outcomes))
names(ipw_models) <- outcomes

for (y in outcomes) {
  fml <- as.formula(paste0(y, " ~ post_intro | county_name + year"))
  ipw_models[[y]] <- feols(fml, data = agg_trim_pca_covid, weights = ~ipw_wt, cluster = "county_name")
}
str(ipw_models)

extract_summary <- function(fit, outcome_name) {
  td <- broom::tidy(fit) %>%
    filter(term == "post_intro") %>%
    transmute(
      outcome  = outcome_name,
      estimate = estimate,
      se       = std.error,
      CI_lo    = estimate - 1.96 * std.error,
      CI_hi    = estimate + 1.96 * std.error
    )
  return(td)
}

results_df <- bind_rows(
  lapply(names(ipw_models), function(y) {
    extract_summary(ipw_models[[y]], outcome_name = y)
  })
)
print(results_df)

res_tex <- kable(
  results_df,
  format   = "latex",
  booktabs = TRUE,
  digits   = c(0, 1, 1, 1, 1),
  caption  = "IPW‐TWFE Estimates of Yelp’s Effect, by Outcome",
  col.names = c(
    "Outcome",
    "Estimate $\\hat{\\tau}$",
    "Std. Error",
    "95\\% CI Lower",
    "95\\% CI Upper"
  )
)
cat(res_tex)
writeLines(res_tex, con = "ipw_twfe_estimates.tex")

```

```{r}
never_treated <- agg_trim_pca_covid %>%
  filter(is.na(first_review))

large_never_full <- never_treated %>%
  group_by(county_name, state_name) %>%
  summarise(
    max_emp       = max(emp, na.rm = TRUE),
    max_total_pop = max(total_pop, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(max_emp))

head(large_never_full, 20)

to_drop <- large_never_full %>%
  filter(max_emp >= 300000) %>%
  pull(county_name)
length(to_drop)

df_trim2 <- agg_trim_pca_covid %>%
  filter(!(county_name %in% to_drop)) %>%
  mutate(
    county_id = as.integer(factor(county_name)),
    g         = if_else(is.na(first_review), 0L, as.integer(first_review))
  )

set.seed(42)  # bootstrap reproducibility
did_trim2 <- att_gt(
  yname         = "emp",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4,
  data          = df_trim2,
  control_group = "notyettreated",
  est_method    = "dr",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE,
  clustervars   = "county_id"
)

agg_att_trim2 <- aggte(did_trim2, type = "simple", na.rm = TRUE)
print(agg_att_trim2)

```


```{r}
treated_sizes <- agg_trim_pca_covid %>%
  filter(!is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_emp = max(emp, na.rm = TRUE), max_pop = max(total_pop, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(max_emp))

head(treated_sizes, 10)

p75_treated_emp <- quantile(treated_sizes$max_emp, probs = 0.75)
p90_treated_emp <- quantile(treated_sizes$max_emp, probs = 0.90)

p75_treated_emp
p90_treated_emp

never_treated <- agg_trim_pca_covid %>%
  filter(is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_emp = max(emp, na.rm = TRUE), .groups = "drop")

controls_to_drop_75 <- never_treated %>%
  filter(max_emp > p75_treated_emp) %>%
  pull(county_name)
length(controls_to_drop_75)

df_trim3 <- agg_trim_pca_covid %>%
  filter(!(county_name %in% controls_to_drop_75)) %>%
  mutate(
    county_id = as.integer(factor(county_name)),
    g         = if_else(is.na(first_review), 0L, as.integer(first_review))
  )

set.seed(42)
did_trim3 <- att_gt(
  yname         = "emp",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4,
  data          = df_trim3,
  control_group = "notyettreated",
  est_method    = "dr",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE,
  clustervars   = "county_id"
)

agg_att_trim3 <- aggte(did_trim3, type = "simple", na.rm = TRUE)
print(agg_att_trim3)

```


```{r}
treated_sizes_est <- agg_trim_pca_covid %>%
  filter(!is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_est = max(est, na.rm = TRUE), .groups = "drop")

p75_treated_est <- quantile(treated_sizes_est$max_est, probs = 0.75, na.rm = TRUE)

controls_to_drop_est <- agg_trim_pca_covid %>%
  filter(is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_est = max(est, na.rm = TRUE), .groups = "drop") %>%
  filter(max_est > p75_treated_est) %>%
  pull(county_name)

df_trim_est <- agg_trim_pca_covid %>%
  filter(!(county_name %in% controls_to_drop_est)) %>%
  mutate(
    county_id = as.integer(factor(county_name)),
    g         = if_else(is.na(first_review), 0L, as.integer(first_review))
  )

set.seed(42)
did_trim_est <- att_gt(
  yname         = "est",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
  data          = df_trim_est,
  control_group = "notyettreated",
  est_method    = "dr",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE,
  clustervars   = "county_id"
)

agg_att_trim_est <- aggte(did_trim_est, type = "simple", na.rm = TRUE)
print(agg_att_trim_est)

```


```{r}
treated_sizes_ap <- agg_trim_pca_covid %>%
  filter(!is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_ap = max(ap, na.rm = TRUE), .groups = "drop")

p75_treated_ap <- quantile(treated_sizes_ap$max_ap, probs = 0.75, na.rm = TRUE)

controls_to_drop_ap <- agg_trim_pca_covid %>%
  filter(is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_ap = max(ap, na.rm = TRUE), .groups = "drop") %>%
  filter(max_ap > p75_treated_ap) %>%
  pull(county_name)

df_trim_ap <- agg_trim_pca_covid %>%
  filter(!(county_name %in% controls_to_drop_ap)) %>%
  mutate(
    county_id = as.integer(factor(county_name)),
    g         = if_else(is.na(first_review), 0L, as.integer(first_review))
  )

set.seed(42)
did_trim_ap <- att_gt(
  yname         = "ap",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
  data          = df_trim_ap,
  control_group = "notyettreated",
  est_method    = "dr",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE,
  clustervars   = "county_id"
)

agg_att_trim_ap <- aggte(did_trim_ap, type = "simple", na.rm = TRUE)
print(agg_att_trim_ap)

did_trim75 <- att_gt(
  yname         = "ap",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
  data          = df_trim75,
  control_group = "notyettreated",
  est_method    = "dr",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE,
  clustervars   = "county_id"
)

agg_att_trim75 <- aggte(did_trim75, type = "simple", na.rm = TRUE)
print(agg_att_trim75)

```

```{r}
treated_sizes_qp1 <- agg_trim_pca_covid %>%
  filter(!is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_qp1 = max(qp1, na.rm = TRUE), .groups = "drop")

p75_treated_qp1 <- quantile(treated_sizes_qp1$max_qp1, probs = 0.75, na.rm = TRUE)

controls_to_drop_qp1 <- agg_trim_pca_covid %>%
  filter(is.na(first_review)) %>%
  group_by(county_name) %>%
  summarise(max_qp1 = max(qp1, na.rm = TRUE), .groups = "drop") %>%
  filter(max_qp1 > p75_treated_qp1) %>%
  pull(county_name)

df_trim_qp1 <- agg_trim_pca_covid %>%
  filter(!(county_name %in% controls_to_drop_qp1)) %>%
  mutate(
    county_id = as.integer(factor(county_name)),
    g         = if_else(is.na(first_review), 0L, as.integer(first_review))
  )

set.seed(42)
did_trim_qp1 <- att_gt(
  yname         = "qp1",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
  data          = df_trim_qp1,
  control_group = "notyettreated",
  est_method    = "dr",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE,
  clustervars   = "county_id"
)

agg_att_trim_qp1 <- aggte(did_trim_qp1, type = "simple", na.rm = TRUE)
print(agg_att_trim_qp1)

```



```{r}
min_year <- min(agg_trim_pca$year)
first_intro %>%
  filter(first_review <= min_year) %>%
  summarise(n_treated_immediately = n())

did_df_es <- agg_trim_pca %>%
  left_join(first_intro, by = "county_name") %>%
  filter(is.finite(first_review), first_review > min_year) %>%
  mutate(
    event_time = year - first_review,
    ev_f       = factor(ifelse(event_time >= -4 & event_time <= 4, event_time, NA), levels = as.character(-4:4))
  ) %>%
  filter(!is.na(ev_f))

old_opts <- options(scipen = 10)
es_rev_clean <- feols(
  avg_log_reviews ~ i(ev_f, ref = "-1") | county_name + year,
  cluster = ~county_name,
  data    = did_df_es
)
iplot(
  es_rev_clean,
  xlab = "Years since Yelp arrives",
  main = "Event‐Study: log reviews (±4 yrs), truly new counties",
  ylim = c(-150000, 150000)
)
options(old_opts)

```

```{r}
df <- agg_trim_pca
thr60 <- df %>%
  filter(avg_log_reviews > 0) %>%
  pull(avg_log_reviews) %>%
  quantile(0.6, na.rm = TRUE)

first_treat60 <- df %>%
  group_by(county_name) %>%
  summarise(first_year60 = min(year[avg_log_reviews > thr60], na.rm = TRUE), .groups = "drop") %>%
  mutate(first_year60 = na_if(first_year60, Inf))

did_df <- df %>%
  left_join(first_rev_df,  by = "county_name") %>%
  left_join(first_treat60, by = "county_name") %>%
  mutate(
    treated60  = as.integer(!is.na(first_year60)),
    post60     = as.integer(year >= first_year60),
    did_bin60  = treated60 * post60,
    post_intro = as.integer(year >= first_review)
  )

iv_emp60 <- feols(
  emp ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin60 ~ post_intro,
  data    = did_df,
  cluster = ~county_name
)
summary(iv_emp60, stage = 1)
summary(iv_emp60, stage = 2)

iv_est60 <- feols(
  est ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin60 ~ post_intro,
  data    = did_df,
  cluster = ~county_name
)
summary(iv_est60, stage = 1)
summary(iv_est60, stage = 2)

iv_ap60 <- feols(
  ap ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin60 ~ post_intro,
  data    = did_df,
  cluster = ~county_name
)
summary(iv_ap60, stage = 1)
summary(iv_ap60, stage = 2)

iv_qp60 <- feols(
  qp1 ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin60 ~ post_intro,
  data    = did_df,
  cluster = ~county_name
)
summary(iv_qp60, stage = 1)
summary(iv_qp60, stage = 2)

etable(
  iv_emp60, iv_est60, iv_ap60, iv_qp60,
  se   = "cluster",
  dict = c(
    did_bin60  = "High‐review DiD (60th pct)",
    post_intro = "Yelp arrival (instr.)",
    PC1        = "Demog. factor 1",
    PC2        = "Demog. factor 2",
    PC3        = "Demog. factor 3",
    PC4        = "Demog. factor 4"
  ),
  title = "IV‐DiD: Yelp Arrival → 60th‐Pctile Treatment → County Outcomes"
)

```

```{r}
did_df <- did_df %>%
  mutate(
    region_name = as.factor(as.character(region_name)),
    region_year = interaction(region_name, year, drop = TRUE)
  )

iv_emp75_regY <- feols(
  emp ~ PC1 + PC2 + PC3 + PC4 | county_name + region_year | did_bin75 ~ post_intro,
  data    = did_df,
  cluster = ~county_name
)
summary(iv_emp75_regY, stage = 1)
summary(iv_emp75_regY, stage = 2)

```


```{r}
did_df <- did_df %>%
  mutate(
    region_name = as.factor(as.character(region_name)),
    region_year = interaction(region_name, year, drop = TRUE)
  )

iv_emp75_regY <- feols(
  emp ~ PC1 + PC2 + PC3 + PC4 | county_name + region_year | did_bin75 ~ post_intro,
  data    = did_df,
  cluster = ~county_name
)
summary(iv_emp75_regY, stage = 1)
summary(iv_emp75_regY, stage = 2)

```

```{r}
did_df_raw <- agg_trim_pca %>%
  left_join(first_treat75, by = "county_name") %>%
  left_join(first_rev_df,   by = "county_name") %>%
  mutate(
    treated75  = as.integer(!is.na(first_year75)),
    post75     = as.integer(year >= first_year75),
    did_bin75  = treated75 * post75,
    post_intro = as.integer(year >= first_review)
  )

controls_raw <- c("avg_income_real", "avg_age", "avg_educ", "pct_employed", "pct_female")
rhs_raw <- paste(controls_raw, collapse = " + ")

iv_emp75_raw <- feols(
  as.formula(paste0("emp ~ ", rhs_raw, " | county_name + year | did_bin75 ~ post_intro")),
  data    = did_df_raw,
  cluster = ~county_name
)
summary(iv_emp75_raw, stage = 1)
summary(iv_emp75_raw, stage = 2)

iv_est75_raw <- feols(
  as.formula(paste0("est ~ ", rhs_raw, " | county_name + year | did_bin75 ~ post_intro")),
  data    = did_df_raw,
  cluster = ~county_name
)
summary(iv_est75_raw, stage = 1)
summary(iv_est75_raw, stage = 2)

iv_ap75_raw <- feols(
  as.formula(paste0("ap ~ ", rhs_raw, " | county_name + year | did_bin75 ~ post_intro")),
  data    = did_df_raw,
  cluster = ~county_name
)
summary(iv_ap75_raw, stage = 1)
summary(iv_ap75_raw, stage = 2)

iv_qp75_raw <- feols(
  as.formula(paste0("qp1 ~ ", rhs_raw, " | county_name + year | did_bin75 ~ post_intro")),
  data    = did_df_raw,
  cluster = ~county_name
)
summary(iv_qp75_raw, stage = 1)
summary(iv_qp75_raw, stage = 2)

etable(
  iv_emp75_raw, iv_est75_raw, iv_ap75_raw, iv_qp75_raw,
  se   = "cluster",
  dict = c(
    did_bin75       = "Treated × Post (75th pct)",
    post_intro      = "Yelp arrival (instr.)",
    avg_income_real = "Real income",
    avg_age         = "Mean age",
    avg_educ        = "Avg education",
    pct_employed    = "Pct employed",
    pct_female      = "Pct female"
  ),
  title = "IV-DiD (Raw Controls): Yelp Arrival → 75th-Pctile Treatment → Outcomes"
)

```


```{r}
did_df_cont <- did_df_raw %>%
  mutate(did_cont75 = avg_log_reviews * post75)

iv_emp_cont75 <- feols(emp ~ avg_income_real + avg_age + avg_educ + pct_employed + pct_female | county_name + year | did_cont75 ~ post_intro, data = did_df_cont, cluster = ~county_name)
iv_est_cont75 <- feols(est ~ avg_income_real + avg_age + avg_educ + pct_employed + pct_female | county_name + year | did_cont75 ~ post_intro, data = did_df_cont, cluster = ~county_name)
iv_ap_cont75  <- feols(ap ~ avg_income_real + avg_age + avg_educ + pct_employed + pct_female | county_name + year | did_cont75 ~ post_intro, data = did_df_cont, cluster = ~county_name)
iv_qp_cont75 <- feols(qp1 ~ avg_income_real + avg_age + avg_educ + pct_employed + pct_female | county_name + year | did_cont75 ~ post_intro, data = did_df_cont, cluster = ~county_name)

etable(
  iv_emp_cont75, iv_est_cont75, iv_ap_cont75, iv_qp_cont75,
  se   = "cluster",
  dict = c(
    did_cont75      = "Log‐Reviews×Post (75th pct)",
    post_intro      = "Yelp arrival (instr.)",
    avg_income_real = "Real income",
    avg_age         = "Mean age",
    avg_educ        = "Avg education",
    pct_employed    = "Pct employed",
    pct_female      = "Pct female"
  ),
  title = "Continuous‐Treatment IV‐DiD (75th pct): Yelp Intensity → County Outcomes"
)

ols_emp_cont75 <- feols(emp ~ did_cont75 + PC1 + PC2 + PC3 + PC4 | county_name + year, data = did_df_cont, cluster = ~county_name)
ols_est_cont75 <- feols(est ~ did_cont75 + PC1 + PC2 + PC3 + PC4 | county_name + year, data = did_df_cont, cluster = ~county_name)
ols_ap_cont75  <- feols(ap ~ did_cont75 + PC1 + PC2 + PC3 + PC4 | county_name + year, data = did_df_cont, cluster = ~county_name)
ols_qp_cont75 <- feols(qp1 ~ did_cont75 + PC1 + PC2 + PC3 + PC4 | county_name + year, data = did_df_cont, cluster = ~county_name)

etable(
  ols_emp_cont75, ols_est_cont75, ols_ap_cont75, ols_qp_cont75,
  se   = "cluster",
  dict = c(did_cont75 = "Log‐Reviews×Post (75th pct)"),
  title = "TWFE OLS (no IV): Continuous Yelp Intensity → Outcomes"
)

```


#interpolated version

```{r}
control_imp <- agg_imp %>%
  select(county_name, year, pct_employed, avg_educ, total_pop, pct_female, avg_age, pct_white, avg_income_real) %>%
  na.omit()

pca_imp <- prcomp(control_imp %>% select(-county_name, -year), center = TRUE, scale. = TRUE)
summary(pca_imp)
screeplot(pca_imp, type = "lines")
print(pca_imp$rotation[, 1:4], digits = 2)

scores_imp <- as_tibble(pca_imp$x[, 1:4], rownames = "row_id") %>%
  mutate(row_id = as.integer(row_id))

scores_imp <- bind_cols(control_imp %>% select(county_name, year), scores_imp %>% select(-row_id)) %>%
  rename_with(~ paste0("PC", 1:4), starts_with("PC"))

agg_imp_pca <- agg_imp %>%
  left_join(scores_imp, by = c("county_name", "year"))

pca_summary <- summary(pca_imp)
capture.output(pca_summary, file = "pca_agg_imp_summary.txt")
pdf("pca_agg_imp_screeplot.pdf", width = 7, height = 5)
screeplot(pca_imp, type = "lines")
dev.off()

loadings_4 <- pca_imp$rotation[, 1:4]
write.table(
  round(loadings_4, 3),
  file      = "agg_imp_loadings_PC1_to_PC4.txt",
  sep       = "\t",
  quote     = FALSE,
  row.names = TRUE,
  col.names = NA
)

saveRDS(agg_imp_pca, "agg_imp_pca.rds")
agg_imp_pca <- readRDS("agg_imp_pca.rds")
saveRDS(scores_imp, "pca_scores_interpolated.rds")

```

```{r}
first_intro_imp <- agg_imp_pca %>%
  group_by(county_name) %>%
  summarise(first_review = min(year[num_reviews > 0], na.rm = TRUE), .groups = "drop")

did_imp_df <- agg_imp_pca %>%
  left_join(first_intro_imp, by = "county_name") %>%
  mutate(
    post_intro = as.integer(year >= first_review),
    did_cont   = avg_log_reviews * post_intro
  )

controls <- c("PC1", "PC2", "PC3", "PC4")

thr90_imp <- did_imp_df %>%
  filter(avg_log_reviews > 0) %>%
  pull(avg_log_reviews) %>%
  quantile(0.9, na.rm = TRUE)

first_orig  <- did_imp_df %>%
  group_by(county_name) %>%
  summarise(first_review = min(year[num_reviews > 0], na.rm = TRUE), .groups = "drop")

first_treat90_imp <- did_imp_df %>%
  group_by(county_name) %>%
  summarise(first_year90 = min(year[avg_log_reviews > thr90_imp], na.rm = TRUE), .groups = "drop") %>%
  mutate(first_year90 = na_if(first_year90, Inf))

did_imp_df <- did_imp_df %>%
  left_join(first_orig,      by = "county_name") %>%
  left_join(first_treat90_imp, by = "county_name") %>%
  mutate(
    treated90   = as.integer(!is.na(first_year90)),
    post90      = as.integer(year >= first_year90),
    did_bin90   = treated90 * post90,
    did_cont90  = avg_log_reviews * post90,
    post_intro  = as.integer(year >= first_review)
  )

iv_emp90_imp <- feols(emp ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin90 ~ post_intro, data = did_imp_df, cluster = ~county_name)
iv_est90_imp <- feols(est ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin90 ~ post_intro, data = did_imp_df, cluster = ~county_name)
iv_ap90_imp  <- feols(ap  ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin90 ~ post_intro, data = did_imp_df, cluster = ~county_name)
iv_qp90_imp <- feols(qp1 ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin90 ~ post_intro, data = did_imp_df, cluster = ~county_name)

etable(
  iv_emp90_imp, iv_est90_imp, iv_ap90_imp, iv_qp90_imp,
  se   = "cluster",
  dict = c(
    did_bin90   = "High‐review DiD (90th pct)",
    post_intro  = "Yelp arrival (instr.)",
    PC1         = "Demographic & SES",
    PC2         = "Employment–Edu vs White",
    PC3         = "Population size",
    PC4         = "Female–White balance"
  ),
  title = "IV-DiD (Interpolated): 90th-Pctile Yelp Treatment → County Outcomes"
)

```

```{r}
thr75_imp <- did_imp_df %>%
  filter(avg_log_reviews > 0) %>%
  pull(avg_log_reviews) %>%
  quantile(0.75, na.rm = TRUE)

first_treat75_imp <- did_imp_df %>%
  group_by(county_name) %>%
  summarise(first_year75 = min(year[avg_log_reviews > thr75_imp], na.rm = TRUE), .groups = "drop") %>%
  mutate(first_year75 = na_if(first_year75, Inf))

did_imp_df <- did_imp_df %>%
  left_join(first_orig,     by = "county_name") %>%
  left_join(first_treat75_imp, by = "county_name") %>%
  mutate(
    treated75  = as.integer(!is.na(first_year75)),
    post75     = as.integer(year >= first_year75),
    did_bin75  = treated75 * post75,
    did_cont75 = avg_log_reviews * post75,
    post_intro = as.integer(year >= first_review)
  )

controls <- c("PC1", "PC2", "PC3", "PC4")

iv_emp75_imp <- feols(emp ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin75 ~ post_intro, data = did_imp_df, cluster = ~county_name)
iv_est75_imp <- feols(est ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin75 ~ post_intro, data = did_imp_df, cluster = ~county_name)
iv_ap75_imp  <- feols(ap  ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin75 ~ post_intro, data = did_imp_df, cluster = ~county_name)
iv_qp75_imp <- feols(qp1 ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_bin75 ~ post_intro, data = did_imp_df, cluster = ~county_name)

etable(
  iv_emp75_imp, iv_est75_imp, iv_ap75_imp, iv_qp75_imp,
  se   = "cluster",
  dict = c(
    did_bin75     = "Treated × Post (75th pct)",
    post_intro    = "Yelp arrival (instr.)",
    PC1            = "Demographic & SES",
    PC2            = "Employment–Edu vs White",
    PC3            = "Population size",
    PC4            = "Female–White balance"
  ),
  title = "IV-DiD (Interpolated): 75th-Pctile Yelp Treatment → County Outcomes"
)

did_imp_cont <- did_imp_df %>%
  mutate(did_cont = avg_log_reviews * post_intro)

iv_emp_cont <- feols(emp ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_cont ~ post_intro, data = did_imp_cont, cluster = ~county_name)
iv_est_cont <- feols(est ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_cont ~ post_intro, data = did_imp_cont, cluster = ~county_name)
iv_ap_cont  <- feols(ap  ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_cont ~ post_intro, data = did_imp_cont, cluster = ~county_name)
iv_qp_cont <- feols(qp1 ~ PC1 + PC2 + PC3 + PC4 | county_name + year | did_cont ~ post_intro, data = did_imp_cont, cluster = ~county_name)

etable(
  iv_emp_cont, iv_est_cont, iv_ap_cont, iv_qp_cont,
  se   = "cluster",
  dict = c(
    did_cont      = "Log‐Reviews × Post",
    post_intro    = "Yelp arrival (instr.)",
    PC1           = "Demog. factor 1",
    PC2           = "Demog. factor 2",
    PC3           = "Demog. factor 3",
    PC4           = "Demog. factor 4"
  ),
  title = "Continuous‐Treatment IV–DiD: Yelp Intensity → County Outcomes"
)

```


#first review
```{r}
add_first_review <- function(df){
  grp_vars <- if ("category_group" %in% names(df)) {
    c("county_name", "category_group")
  } else {
    "county_name"
  }

  df %>%
    group_by(across(all_of(grp_vars))) %>%
    mutate(
      first_review = if_else(
        any(num_reviews > 0, na.rm = TRUE),
        min(year[num_reviews > 0], na.rm = TRUE),
        as.integer(NA)
      ),
      post_intro = as.integer(year >= first_review)
    ) %>%
    ungroup()
}

panels <- list(
  agg_trim    = agg_trim_pca_covid,
  agg_imp     = agg_imp_pca_covid,
  sect_trim   = sect_trim_pca_covid,
  sect_imp    = sect_imp_pca_covid
)

panels_updated <- lapply(panels, add_first_review)

agg_trim_pca  <- panels_updated$agg_trim
agg_imp_pca   <- panels_updated$agg_imp
sect_trim_pca <- panels_updated$sect_trim
sect_imp_pca  <- panels_updated$sect_imp

```

