---
title: "Master file -Reviews part 2"
author: "Manos Giannitselis"
date: "2025-06-01"
output: html_document
---

```{r setup-part2, include=FALSE}
# ── Part 2 requires these packages (standalone-safe library block) ─────────────
required_packages <- c(
  "readr", "dplyr", "ggplot2", "tidyr", "purrr", "stringr", "forcats",
  "lubridate", "zoo", "knitr", "kableExtra", "broom", "did",
  "fixest", "sandwich", "lmtest", "car", "scales"
)
install_missing_packages <- function(pkgs) {
  miss <- pkgs[!pkgs %in% installed.packages()[, "Package"]]
  if (length(miss)) install.packages(miss)
}
install_missing_packages(required_packages)
lapply(required_packages, library, character.only = TRUE)

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# ── Reproducibility ────────────────────────────────────────────────────────────
set.seed(42)

# ── Load all objects produced by Part 1 ───────────────────────────────────────
# These must exist on disk (produced by running Part 1 first).
agg_trim_pca_covid  <- readRDS("agg_trim_pca_covid.rds")
agg_imp_pca_covid   <- readRDS("agg_imp_pca_covid.rds")
sect_trim_pca_covid <- readRDS("sect_trim_pca_covid.rds")
sect_imp_pca_covid  <- readRDS("sect_imp_pca_covid.rds")
panel_full_trim     <- readRDS("full_panel.rds")          # sector-level full panel
panel_full_imp      <- readRDS("sect_panel.rds")          # imputed sector panel
pca                 <- readRDS("pca.rds")                 # PCA object for rotation checks
controls_raw        <- readRDS("controls_raw.rds")        # character vector of control names
n_pcs               <- 4                                  # must match Part 1

# ── Load aggregate DiD objects saved at the end of Part 1 ─────────────────────
# (used in the event-study chunks below)
if (file.exists("did_est.rds"))  did_est  <- readRDS("did_est.rds")
if (file.exists("did_ap.rds"))   did_ap   <- readRDS("did_ap.rds")
if (file.exists("did_qp1.rds"))  did_qp1  <- readRDS("did_qp1.rds")
if (file.exists("did_mod3.rds")) did_mod3 <- readRDS("did_mod3.rds")
```


```{r}
make_ipw_treated <- function(df){
  df2 <- df %>%
    arrange(county_name, year) %>%
    group_by(county_name) %>%
    mutate(
      avg_log_reviews = as.numeric(avg_log_reviews),
      d_review        = avg_log_reviews - lag(avg_log_reviews)
    ) %>%
    ungroup() %>%
    filter(!is.na(d_review), !is.na(PC1), !is.na(PC2), !is.na(PC3), !is.na(PC4))

  mu0    <- mean(df2$d_review)
  sigma0 <- sd(df2$d_review)

  cond_mod  <- lm(d_review ~ PC1 + PC2 + PC3 + PC4, data = df2)
  mu_hat    <- predict(cond_mod, df2)
  sigma_hat <- sd(residuals(cond_mod))

  df2 <- df2 %>%
    mutate(
      log_num   = dnorm(d_review, mu0,    sigma0,    log = TRUE),
      log_den   = dnorm(d_review, mu_hat, sigma_hat, log = TRUE),
      log_wt    = log_num - log_den
    ) %>%
    mutate(
      log_wt_c = log_wt - median(log_wt, na.rm = TRUE),
      ipw_wt   = exp(log_wt_c)
    ) %>%
    mutate(ipw_wt = ipw_wt / mean(ipw_wt, na.rm = TRUE))

  return(df2)
}

panels <- list(
  agg_trim_covid  = agg_trim_pca_covid,
  agg_imp_covid   = agg_imp_pca_covid,
  sect_trim_covid = sect_trim_pca_covid,
  sect_imp_covid  = sect_imp_pca_covid
)
panels_wt_treated <- lapply(panels, make_ipw_treated)

pdf("ipw_weights_histograms.pdf", width = 8, height = 6)
par(mfrow = c(2,2), mar = c(4,4,2,1))
for (name in names(panels_wt_treated)) {
  w <- panels_wt_treated[[name]]$ipw_wt
  hist(w, breaks = 30, main = paste("IPW weights:", name), xlab = "Weight", ylab = "Count")
}
dev.off()

save(
  panels_wt_treated,
  file = "panels_wt_treated.RData"
)

for (name in names(panels_wt_treated)) {
  saveRDS(panels_wt_treated[[name]], file = paste0(name, "_wt.rds"))
}

save(
  agg_trim_pca_covid,
  agg_imp_pca_covid,
  sect_trim_pca_covid,
  sect_imp_pca_covid,
  file = "covid_panels.RData"
)

saveRDS(agg_trim_pca_covid,  "agg_trim_pca_covid.rds")
saveRDS(agg_imp_pca_covid,   "agg_imp_pca_covid.rds")
saveRDS(sect_trim_pca_covid, "sect_trim_pca_covid.rds")
saveRDS(sect_imp_pca_covid,  "sect_imp_pca_covid.rds")

```



```{r}
df <- panels_wt_treated$agg_trim_covid %>%
  filter(!is.na(ipw_wt))

fe_mod <- lm(emp ~ avg_log_reviews + factor(county_name) + factor(year), data = df, weights = ipw_wt)
coeftest(fe_mod, vcov = vcovCL, cluster = ~county_name)
capture.output(summary(fe_mod), file = "fe_mod_summary.txt")
coef_row <- summary(fe_mod)$coefficients["avg_log_reviews", ]
capture.output(coef_row, file = "avg_log_reviews_coef.txt")

```


```{r}
fe_mod <- lm(est ~ avg_log_reviews + factor(county_name) + factor(year), data = df, weights = ipw_wt)
coeftest(fe_mod, vcov = vcovCL, cluster = ~county_name)
capture.output(summary(fe_mod), file = "est_fe_mod_summary.txt")
coef_row <- summary(fe_mod)$coefficients["avg_log_reviews", ]
capture.output(coef_row, file = "est_avg_log_reviews_coef.txt")

```

```{r}
fe_mod2 <- lm(
  est ~ avg_log_reviews + PC1 + PC2 + PC3 + PC4 + factor(county_name) + factor(year),
  data    = df,
  weights = ipw_wt
)
coeftest(fe_mod2, vcov = vcovCL, cluster = ~county_name)
capture.output(summary(fe_mod2), file = "est_fe_mod2_summary.txt")
coef_row <- summary(fe_mod2)$coefficients["avg_log_reviews", ]
capture.output(coef_row, file = "avg_log_reviews_coef2.txt")

```


```{r}
vif(lm(avg_log_reviews ~ PC1 + PC2 + PC3 + PC4, data = df))
for (pc in paste0("PC", 1:4)) {
  f <- as.formula(
    paste("est ~ avg_log_reviews +", paste(setdiff(paste0("PC", 1:4), pc), collapse = " + "), "+ factor(county_name) + factor(year)")
  )
  print(pc)
  print(coeftest(lm(f, data = df, weights = ipw_wt), vcov = vcovCL, cluster = ~county_name)["avg_log_reviews", ])
}
cor(df$avg_log_reviews, df$PC3, use = "pairwise.complete.obs")
summary(pca)$rotation[, "PC3"]

```





```{r}
panel_full_trim <- panel_full_trim %>% 
  mutate(category_group = factor(category_group, 
                         levels = c("Retail","Health","Food","Other")))

df_sec <- panel_full_trim

df_sec <- df_sec %>%
  mutate(
    county_sector = paste(county_name, category_group, sep = "_")
  )

df_sec %>% 
  distinct(county_name, category_group, county_sector) %>% 
  head(10)

```




```{r}

panel_full_trim <- panel_full_trim %>%
  mutate(county_sector = interaction(county_name, category_group, sep="_"))




sect_trim <- panel_full_imp %>%
  filter(if_all(all_of(controls_raw), ~ !is.na(.x))) %>%
  mutate(
    county_sector   = paste(county_name, category_group, sep = "_"),
    num_reviews     = replace_na(num_reviews, 0L),
    avg_log_reviews = replace_na(avg_log_reviews, 0),
    avg_rating      = replace_na(avg_rating, 0)
  )

```

```{r}

control_sec <- sect_trim_pca %>%
  select(county_name, year, category_group,
         pct_employed, avg_educ, total_pop, pct_female,
         avg_age, pct_white, avg_income_real)

pca_input <- control_sec %>%
  select(pct_employed, avg_educ, total_pop, pct_female,
         avg_age, pct_white, avg_income_real)

apply(pca_input, 2, sd, na.rm=TRUE)
apply(pca_input, 2, function(x) length(unique(x)))

pca_sec <- prcomp(pca_input, center = TRUE, scale. = TRUE)


summary(pca_sec)            
screeplot(pca_sec, type="lines")

# 5. Look at the first 4 loadings
print(pca_sec$rotation[, 1:4], digits = 3)


pca_summary <- summary(pca_sec)
capture.output(pca_summary, file = "pca_sec_trim_summary.txt")

pdf("sec_trim_pca_screeplot.pdf", width = 7, height = 5)
screeplot(pca_sec, type = "lines")
dev.off()
#############################

loadings_4 <- pca_sec$rotation[, 1:4]

write.table(
  round(loadings_4, 3),            
  file      = "sect_trim_pca_loadings_PC1_to_PC4.txt",
  sep       = "\t",                
  quote     = FALSE,              
  row.names = TRUE,                
  col.names = NA                  
)

###################################################
scores_sec <- as_tibble(pca_sec$x[,1:4], .name_repair="minimal") %>%
  set_names(paste0("PC", 1:4)) %>%
  bind_cols(control_sec %>% select(county_name, year, category_group))

scores_sec %>%
  count(county_name, year, category_group) %>%
  filter(n > 1)
scores_sec <- scores_sec %>%
  distinct(county_name, year, category_group, .keep_all = TRUE)

# FIX: renamed from sect_trim_pca to sect_trim_pca_sec to avoid overwriting the
# aggregate-level sect_trim_pca object defined earlier in this script.
sect_trim_pca_sec <- sect_trim %>%
  left_join(scores_sec,
            by = c("county_name","year","category_group"))

saveRDS(sect_trim_pca_sec, "sect_trim_pca_sec.rds")


```





```{r}
sect_trim_pca %>%
  group_by(category_group, year) %>%
  summarize(
    est_mean = mean(est, na.rm=TRUE),
    est_se   = sd(est, na.rm=TRUE)/sqrt(n()),
    avg_rev  = mean(avg_log_reviews, na.rm=TRUE)
  ) %>%
ggplot(aes(year, est_mean, color=category_group)) +
  geom_line() +
  geom_ribbon(aes(ymin=est_mean-1.96*est_se,
                  ymax=est_mean+1.96*est_se,
                  fill=category_group),
              alpha=0.2) +
  labs(title="County x Sector Establishments over Time",
       y="Mean Establishments", x="Year")

```


```{r}
sect_trim_pca %>%
  filter(!is.na(post_intro)) %>%
  group_by(category_group) %>%
  filter(any(post_intro == 0) && any(post_intro == 1)) %>%
  do(tidy(t.test(emp ~ post_intro, data = .))) %>%
  select(
    category_group,
    mean_pre   = estimate2,  
    mean_post  = estimate1,  
    t_stat     = statistic,
    p_value    = p.value
  )

```


```{r}
# FIX: replaced stale 'sect2' with 'sect_trim_pca' and 'post_intro_sec' with 'post_intro'
sect_trim_pca %>% 
  filter(!is.na(post_intro)) %>% 
  group_by(category_group) %>% 
  summarize(
    n_pre  = sum(post_intro == 0),
    n_post = sum(post_intro == 1)
  ) %>% 
  filter(n_pre > 0 & n_post > 0)

```


```{r}
library(forcats)

sect_trim_pca_clean <- sect_trim_pca %>%
  mutate(
    # FIX: fct_explicit_na() is deprecated since forcats 1.0 — use fct_na_value_to_level()
    category_group = fct_na_value_to_level(category_group, level = "NoReviews")
  ) %>%
  
  mutate(
    first_review = if_else(is.infinite(first_review), NA_real_, first_review),
    
    event_time   = if_else(
                     is.na(first_review),
                     NA_real_,
                     year - first_review
                   ),
    
    post_intro   = if_else(
                     is.na(first_review),
                     0L, 
                     as.integer(year >= first_review)
                   )
  )

```


```{r}
sect_trim_pca<-sect_trim_pca_clean
sect_trim_pca %>% 
  summarize(
    n_inf_event = sum(is.infinite(event_time)),
    n_na_event  = sum(is.na(event_time)),
    n_inf_first = sum(is.infinite(first_review)),
    n_na_first  = sum(is.na(first_review))
  )
valid_sectors <- sect_trim_pca %>% 
  group_by(category_group) %>% 
  filter(any(post_intro==0) && any(post_intro==1)) %>% 
  pull(category_group) %>% unique()

means_by_sector <- sect_trim_pca %>% 
  filter(category_group %in% valid_sectors) %>% 
  group_by(category_group) %>% 
  do({
    test = t.test(emp ~ post_intro, data = .)
    tibble(
      mean_pre  = test$estimate["mean in group 0"],
      mean_post = test$estimate["mean in group 1"],
      t_stat    = test$statistic,
      p_value   = test$p.value
    )
  }) %>% 
  ungroup()

means_by_sector

#######

sect_trim_pca %>%
  mutate(et = as.numeric(as.character(event_time))) %>%
  filter(et < 0) %>%
  tally(name = "n_pre_obs")

sect_trim_pca %>%
  mutate(et = as.numeric(as.character(event_time))) %>%
  filter(et < 0) %>%
  distinct(county_name) %>%
  tally(name = "n_counties_pre")

sect_check <- panel_full_imp %>%        
  left_join(
    first_intro_sec,                   
    by = c("county_name","category_group")
  ) %>%
 
  mutate(
    event_time = year - first_rev_sec
  ) %>%
  filter(is.finite(event_time)) 

sect_check %>%
  group_by(category_group, period = if_else(event_time < 0, "pre", "post")) %>%
  summarize(n = n(), .groups = "drop") %>%
  pivot_wider(names_from = period, values_from = n)
sect_check %>%
  group_by(category_group, event_time) %>%
  tally() %>%
  print(n = Inf)

#Food

food_df <- sect_trim_pca %>% 
  filter(category_group == "Food", 
         !is.na(event_time)) %>% 
  mutate(post = event_time >= 0)

food_df %>% 
  count(post)



food_df %>% 
  group_by(post) %>% 
  summarize(
    mean_reviews = mean(avg_log_reviews, na.rm=TRUE),
    n            = n()
  )



```

```{r}

es_sec <- sect_trim_pca %>% 

  filter(!is.na(event_time) & between(event_time, -4, +4)) 

es_mod_sec <- feols(
  est ~ i(event_time, ref = -1) 
      | county_sector + year,      
  cluster = ~county_sector,
  data    = es_sec
)

iplot(
  es_mod_sec, 
  xlab = "Years since first Yelp review (sector)", 
  main = "Event Study: Establishments (±4 yrs) by Sector"
)

```



```{r}
sect_trim_pca %>%
  group_by(category_group, year) %>%
  summarize(
    emp_var = var(emp, na.rm=TRUE), 
    rev_var = var(avg_log_reviews, na.rm=TRUE)
  ) %>%
  pivot_longer(c(emp_var, rev_var), names_to="metric", values_to="v") %>%
  ggplot(aes(year, v, color=metric)) +
    geom_line() +
    facet_wrap(~category_group) +
    labs(title="Variance of Reviews vs. Employment by Sector")

```


```{r}
first_intro <- panel_full_imp %>% 
  group_by(county_name) %>%
  summarize(
    first_review = min(year[num_reviews > 0], na.rm = TRUE),
    .groups      = "drop"
  )

sect_trim_pca <- sect_trim_pca %>% 
  left_join(first_intro, by="county_name")

```


```{r}
sect_trim_pca <- sect_trim_pca %>%
  mutate(
    post_intro = as.integer(year >= first_review), 
    event_time = year - first_review
  )

```


#heterogeneity by sector
```{r}
feols(
  emp ~ i(category_group, did_bin)  + PC1+PC2+PC3+PC4
  | county_sector + year,
  data    = sect_trim_pca,
  cluster = ~county_name
)

```

```{r}
map(levels(sect_trim_pca$category_group), ~
  feols(
    emp ~ post_intro | county_name + year,
    data = filter(sect_trim_pca, category_group==.x),
    cluster="county_name"
  ) %>% coefplot(main=.x)
)

```

```{r}
controls <- c(
  "avg_income_real", "avg_income",
  "avg_age",         "avg_educ",
  "pct_employed",    "pct_female",
  "pct_white",       "total_pop"
)
sect_imp <- panel_full_imp %>% 
  arrange(county_name, category_group, year) %>% 
  group_by(county_name, category_group) %>% 
  mutate(
    across(
      all_of(controls),
      ~ na.approx(
          .x,
          x      = year,
          na.rm  = FALSE,
          rule   = 2    
        )
    )
  ) %>% 
  ungroup()

sect_imp %>% 
  summarise(across(
    all_of(controls),
    ~ sum(is.na(.)),
    .names = "nNA_{col}"
  ))

#save it
saveRDS(sect_imp, "sect_imp.rds")
sect_imp <- readRDS("sect_imp.rds")

```


```{r}
sect_trim_pca %>% 
  summarise(across(
    all_of(controls),
    ~ sum(is.na(.)),
    .names = "nNA_{col}"
  ))

```


```{r}

control_sec <- sect_imp_covid %>%
  select(county_name, year, category_group,
         pct_employed, avg_educ, total_pop, pct_female,
         avg_age, pct_white, avg_income_real)

pca_input <- control_sec %>%
  select(pct_employed, avg_educ, total_pop, pct_female,
         avg_age, pct_white, avg_income_real)


apply(pca_input, 2, sd, na.rm=TRUE)
apply(pca_input, 2, function(x) length(unique(x)))
pca_sec <- prcomp(pca_input, center = TRUE, scale. = TRUE)
summary(pca_sec)            
screeplot(pca_sec, type="lines")

print(pca_sec$rotation[, 1:4], digits = 3)

########
pca_summary <- summary(pca_sec)
capture.output(pca_summary, file = "pca_sec_imp_summary.txt")

pdf("pca_sec_imp_screeplot.pdf", width = 7, height = 5)
screeplot(pca_sec, type = "lines")
dev.off()

# extract the first 4 loadings
loadings_4 <- pca_sec$rotation[, 1:4]

write.table(
  round(loadings_4, 3),            
  file      = "sect_imp_pca_loadings_PC1_to_PC4.txt",
  sep       = "\t",                
  quote     = FALSE,               
  row.names = TRUE,               
  col.names = NA                   
)

scores_sec <- as_tibble(pca_sec$x[,1:4], .name_repair="minimal") %>%
  set_names(paste0("PC", 1:4)) %>%
  bind_cols(control_sec %>% select(county_name, year, category_group))

scores_sec %>%
  count(county_name, year, category_group) %>%
  filter(n > 1)
scores_sec <- scores_sec %>%
  distinct(county_name, year, category_group, .keep_all = TRUE)

sect_imp_pca_covid <- sect_imp_covid %>%
  left_join(scores_sec,
            by = c("county_name","year","category_group"))

saveRDS(sect_imp_pca_covid, "sect_imp_pca_covid.rds")
sect_trim_pca_covid <- readRDS("sect_trim_pca_covid.rds")

```


#Callaway and Sant'Anna

```{r}
df <- panels_wt_treated$agg_trim_covid   

df <- panels_wt_treated$agg_trim_covid %>%
  arrange(county_name, year) %>%
  group_by(county_name) %>%
  mutate(
    d_emp = emp - dplyr::lag(emp)
  ) %>%
  ungroup() %>%
  filter(!is.na(d_emp), !is.na(d_review))

summary(df$d_emp)
head(df[, c("county_name","year","emp","d_emp")], 10)

#OLS
outcome_mod <- lm(
  d_emp ~ d_review + PC1 + PC2 + PC3 + PC4,
  data = df
)
summary(outcome_mod)

```

```{r}
df <- df %>%
  mutate(mu_hat_emp = predict(outcome_mod, newdata = df),
         resid_emp  = d_emp - mu_hat_emp)

summary(df$mu_hat_emp)
summary(df$resid_emp)

```

```{r}
df <- df %>%
  mutate(
    dr_score = mu_hat_emp   + 
               ipw_wt   * (d_emp - mu_hat_emp)
  )
summary(df$dr_score)
hist(df$dr_score, breaks=30, main="DR Scores", xlab="dr_score")

```


```{r}
df <- df %>%
  mutate(
    dr_score = mu_hat_emp   + 
               ipw_wt   * (d_emp - mu_hat_emp)
  )
summary(df$dr_score)
hist(df$dr_score, breaks=30, main="DR Scores", xlab="dr_score")

```


```{r}
dr_mod <- lm(dr_score ~ d_review, data = df)
summary(dr_mod)

df_bins <- df %>%
  mutate(
    bin = ntile(d_review, 4),                    
    mid = ave(d_review, bin, FUN = mean)         
  )

dose_resp <- df_bins %>%
  group_by(bin, mid) %>%
  summarize(
    avg_dr = mean(dr_score, na.rm = TRUE),
    n_obs  = n(),
    .groups = "drop"
  )

print(dose_resp)

plot(
  dose_resp$mid, dose_resp$avg_dr,
  type = "b", pch = 16,
  xlab = "Δ avg_log_reviews (bin midpoint)",
  ylab = "Average DR Score (Δ emp)",
  main = "Binned Dose–Response"
)

```

```{r}
dose_resp_ci <- df_bins %>%
  group_by(bin, mid) %>%
  summarize(
    avg_dr = mean(dr_score, na.rm = TRUE),
    sd_dr  = sd(dr_score,   na.rm = TRUE),
    n_obs  = n(),
    se_dr  = sd_dr / sqrt(n_obs),
    # 95% CI:
    ci_lo  = avg_dr - 1.96 * se_dr,
    ci_hi  = avg_dr + 1.96 * se_dr,
    .groups = "drop"
  )

print(dose_resp_ci)

with(dose_resp_ci, {
  plot(mid, avg_dr, ylim = range(ci_lo, ci_hi),
       pch = 16, xlab = "Δ avg_log_reviews", ylab = "Avg Δ emp",
       main = "Dose–Response with 95% CI")
  arrows(mid, ci_lo, mid, ci_hi, angle = 90, code = 3, length = 0.05)
})

```

```{r}
df <- df %>%
  arrange(county_name, year) %>%
  group_by(county_name) %>%
  mutate(
    d_emp_lag = dplyr::lag(d_emp)
  ) %>%
  ungroup() %>%
  filter(!is.na(d_emp), !is.na(d_emp_lag))

outcome_mod3 <- lm(
  d_emp ~ d_review 
         + d_emp_lag
         + PC1 + PC2 + PC3 + PC4
         + covid_case_pct + covid_death_pct,
  data = df
)
summary(outcome_mod3)

```


#did
```{r did-setup}
# FIX: removed broken install.packages() calls with stray ')' syntax error.
# Packages are now loaded in the setup-part2 chunk at the top of this file.

agg_trim_pca_covid <- agg_trim_pca_covid %>%
  mutate(
    g = if_else(is.na(first_review), 
                0L,                
                as.integer(first_review))
  )
```
  yname         = "emp",
  tname         = "year_num",
  idname        = "county_id",
  gname         = "g",                  
  xformla       = ~ PC1 + PC2 + PC3 + PC4,
  data          = agg_trim_pca_covid,
  control_group = "notyettreated",       
  est_method    = "dr",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE
)
panel <- panels_wt_treated$agg_trim_covid %>%
  mutate(year = as.integer(year)) %>%
  mutate(
    county_id = as.integer(factor(county_name)),
    g         = if_else(is.na(first_review), 0L, as.integer(first_review))
  )

names(panel)

set.seed(42)  # bootstrap reproducibility
did_mod2 <- att_gt(
  yname         = "emp",
  tname         = "year",          
  idname        = "county_id",
  gname         = "g",              
  xformla       = ~ PC1 + PC2 + PC3 + PC4,
  data          = panel,
  control_group = "notyettreated",
  weightsname   = "ipw_wt",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE
)

dr_data <- did_mod2$DIDparams$data
summary(dr_data$.w)
summary(did_mod2)

```

```{r}
trim.emp.sdidpc <- summary(did_mod2)

saveRDS(trim.emp.sdidpc, file = "trim.emp.sdidpc.rds")

capture.output(
  trim.emp.sdidpc,
  file = "trim.emp.sdidpc.txt"
)

agg_att <- aggte(did_mod2,
                 type    = "simple",
                 na.rm   = TRUE)    
summary(agg_att)

```






```{r}
pre_trends <- with(es, 
  data.frame(
    event_time = egt, 
    att        = att.egt, 
    se         = se.egt,
    ci_lo      = att.egt - 1.96 * se.egt,
    ci_hi      = att.egt + 1.96 * se.egt
  )
)

pre_trends <- pre_trends[pre_trends$event_time < 0, ]

pre_trends

```

```{r}
pre_effects <- tibble(
  event_time = es$egt,
  att         = es$att.egt,
  se          = es$se.egt
) %>%
  filter(event_time < 0) %>%
  mutate(
    ci_lo       = att - 1.96 * se,
    ci_hi       = att + 1.96 * se,
    significant = !(ci_lo <= 0 & ci_hi >= 0)
  )

print(pre_effects)
```




```{r}
agg_att <- aggte(did_mod2, type = "simple", na.rm = TRUE)
summary(agg_att)

saveRDS(agg_att, file = "agg_att_trim.emp.sdidpc.rds")
write.csv(as.data.frame(agg_att), "agg_att_trim.emp.sdidpc.csv", row.names = FALSE)

```


```{r}
agg_att_df <- data.frame(
  ATT   = agg_att$overall.att,
  SE    = agg_att$overall.se,
  CI_lo = agg_att$overall.att - 1.96 * agg_att$overall.se,
  CI_hi = agg_att$overall.att + 1.96 * agg_att$overall.se
)

agg_att_df

```

```{r}
agg_trim_pca_covid <- agg_trim_pca_covid %>%
  mutate(region = factor(region_name)) 

set.seed(42)
did_mod3 <- att_gt(

summary(did_mod3)

agg_att3 <- aggte(did_mod3, type = "simple", na.rm = TRUE)

summary(agg_att3)

```


```{r event-study-emp-regionFE-ggplot}
# FIX: ggplot2 replaces base-R plot()/arrows() for the region FE event study
es3 <- aggte(did_mod3, type = "dynamic", na.rm = TRUE)

df_es3 <- tibble(
  event_time = es3$egt,
  att        = es3$att.egt,
  se         = es3$se.egt
) |>
  mutate(ci_low = att - 1.96 * se, ci_high = att + 1.96 * se)

p_es3 <- ggplot(df_es3, aes(x = event_time, y = att)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.15, fill = "steelblue") +
  geom_line(color = "steelblue", linewidth = 0.8) +
  geom_point(color = "steelblue", size = 2) +
  scale_x_continuous(breaks = unique(df_es3$event_time)) +
  labs(
    title = "Event Study with Region FE",
    x     = "Years since Yelp entry",
    y     = "ATT(emp)"
  ) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))

print(p_es3)
ggsave("event_study_emp_regionFE.pdf", plot = p_es3, width = 8, height = 6)
```

```{r}
fe_sunab <- feols(
  dr_score ~ sunab(first_review, year) 
  | county_name + year,
  data    = df,
  weights = ~ ipw_wt
)

iplot(fe_sunab,
      main = "Weighted TWFE Event Study",
      xlab = "Years Since Yelp Entry",
      ylab = "ATT(emp)")

```

```{r}
df_wt <- panels_wt_treated$agg_trim_covid

df_diff <- df_wt %>%
  arrange(county_name, year) %>%
  group_by(county_name) %>%
  mutate(
    d_emp    = emp - lag(emp),
    d_review = avg_log_reviews - lag(avg_log_reviews)
  ) %>%
  ungroup() %>%
  filter(
    !is.na(d_emp),
    !is.na(d_review),
    !is.na(ipw_wt)
  )

fe_diff_wt <- feols(
  d_emp    ~ d_review
    | county_name + year,
  data    = df_diff,
  weights = ~ ipw_wt,
  cluster = ~ county_name
)

summary(fe_diff_wt)

```

```{r}
df_all <- panels_wt$agg_trim %>%
  mutate(post_intro = if_else(is.na(first_review), 0L, as.integer(year >= first_review)))

fe_plain <- feols(
  ap ~ post_intro
    | county_name + year,
  data    = df_all,
  cluster = ~ county_name
)

summary(fe_plain)

```


```{r}
ps_mod <- glm(
  I(!is.na(first_review)) ~ PC1 + PC2 + PC3 + PC4 + region_name,
  family = binomial(),
  data   = df_all
)

df_all <- df_all %>%
  mutate(
    ps    = predict(ps_mod, type = "response"),
    ipw2  = if_else(
      post_intro == 1,
      1 / ps,
      1 / (1 - ps)
    )
  )

table(is.na(df_all$ipw2))

fe_ipw_bin <- feols(
  emp ~ post_intro
    | county_name + year,
  data    = df_all,
  weights = ~ ipw2,
  cluster = ~ county_name
)

summary(fe_ipw_bin)

```

#est
```{r}
set.seed(42)
did_est <- att_gt(
  yname         = "est",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",                # first_review group
  xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
  data          = agg_trim_pca_covid,
  control_group = "notyettreated",
  est_method    = "dr",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE
)
summary(did_est)
saveRDS(did_est, "did_est.rds")

es_est <- aggte(did_est, type="dynamic", na.rm = TRUE)
agg_est <- aggte(did_est, type="simple", na.rm = TRUE)
summary(agg_est)

```



```{r}
trimmed <- dr_data %>%
  filter(.w >= 0.1, .w <= 10)

did_trimmed <- att_gt(
  yname         = "emp",
  tname         = "year_num",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4,
  data          = trimmed,
  control_group = "notyettreated",
  est_method    = "dr",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE
)

summary(did_trimmed)

```


```{r}
df_all <- df_all %>%
  mutate(
    region_name = factor(region_name)
  )

fe_regional_ts <- feols(
  emp ~ post_intro 
    | county_name + year + region_name:year,
  data    = df_all,
  cluster = ~ county_name
)
summary(fe_regional_ts)

```


```{r}
did_est_reg <- att_gt(
  yname         = "est",
  tname         = "year",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
  data          = agg_trim_pca_covid,
  control_group = "notyettreated",
  est_method    = "dr",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE
)
summary(aggte(did_est_reg, type="simple", na.rm=TRUE))

```


```{r}
pre_est <- aggte(did_est_reg, type = "dynamic", na.rm = TRUE)
df_pre_est <- data.frame(
  event_time = pre_est$egt,
  att        = pre_est$att.egt,
  se         = pre_est$se.egt
)

# 3) Subset to t = -4,…,-1
df_pre_est[df_pre_est$event_time < 0, ]

```

```{r}
agg_trim_pca_covid %>%
  group_by(region_name) %>%
  summarize(
    mean_PC1 = mean(PC1, na.rm = TRUE),
    mean_PC2 = mean(PC2, na.rm = TRUE),
    mean_PC3 = mean(PC3, na.rm = TRUE),
    mean_PC4 = mean(PC4, na.rm = TRUE),
    .groups = "drop"
  )

```

```{r}
summary(lm(PC1 ~ region_name, data = agg_trim_pca_covid))$r.squared

```

```{r}
es_est <- aggte(did_est_reg, type = "dynamic", na.rm = TRUE)
with(es_est, {
  plot(egt, att.egt,
       type = "b", pch = 16, lwd = 1.5,
       xlab = "Years Since Yelp Entry",
       ylab = "ATT(est)",
       main = "Event Study: Yelp Entry → Establishments")
  arrows(x0 = egt,
         y0 = att.egt - 1.96 * se.egt,
         x1 = egt,
         y1 = att.egt + 1.96 * se.egt,
         angle = 90, code = 3, length = 0.05)
  abline(h = 0, lty = 2, col = "gray")
})

agg_est <- aggte(did_est_reg, type = "simple", na.rm = TRUE)

agg_est_df <- data.frame(
  ATT   = agg_est$overall.att,
  SE    = agg_est$overall.se,
  CI_lo = agg_est$overall.att - 1.96 * agg_est$overall.se,
  CI_hi = agg_est$overall.att + 1.96 * agg_est$overall.se
)
agg_est

```

```{r event-study-est-ggplot}
# FIX: replaced base-R plot()/arrows() with ggplot2 for consistency and cleaner export
es_est <- aggte(did_est_reg, type = "dynamic", na.rm = TRUE)

df_es_est <- tibble(
  event_time = es_est$egt,
  att        = es_est$att.egt,
  se         = es_est$se.egt
) |>
  mutate(
    ci_low  = att - 1.96 * se,
    ci_high = att + 1.96 * se
  )

p_es_est <- ggplot(df_es_est, aes(x = event_time, y = att)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_vline(xintercept = -0.5, linetype = "dotted", color = "gray70") +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.15, fill = "steelblue") +
  geom_line(color = "steelblue", linewidth = 0.8) +
  geom_point(color = "steelblue", size = 2) +
  scale_x_continuous(breaks = unique(df_es_est$event_time)) +
  labs(
    title = "Event-Study: Yelp Entry → Establishments",
    x     = "Years Since Yelp Entry",
    y     = "ATT(est)"
  ) +
  theme_bw() +
  theme(
    plot.title   = element_text(hjust = 0.5),
    axis.text.x  = element_text(angle = 45, hjust = 1)
  )

print(p_es_est)
ggsave("es_establishments.pdf", plot = p_es_est, width = 6, height = 4)

agg_est <- aggte(did_est_reg, type = "simple", na.rm = TRUE)
agg_est_df <- data.frame(
  outcome = "est",
  ATT     = agg_est$overall.att,
  SE      = agg_est$overall.se,
  CI_lo   = agg_est$overall.att - 1.96 * agg_est$overall.se,
  CI_hi   = agg_est$overall.att + 1.96 * agg_est$overall.se
)
print(agg_est_df)
write.csv(agg_est_df, "aggregate_ATT_establishments.csv", row.names = FALSE)
writeLines(
  kable(agg_est_df, format = "latex", booktabs = TRUE,
        caption = "Aggregate ATT: Yelp Entry → Establishments"),
  "aggregate_ATT_establishments.tex"
)
```


```{r}
did_est <- att_gt(
  yname         = "est",
  tname         = "year_num",
  idname        = "county_id",
  gname         = "g",
  xformla       = ~ PC1 + PC2 + PC3 + PC4,
  data          = agg_trim_pca_covid,
  control_group = "notyettreated",
  est_method    = "dr",
  bstrap        = TRUE,
  biters        = 200,
  cband         = TRUE
)

pre_est <- aggte(did_est, type = "dynamic", na.rm = TRUE)
df_pre_est <- data.frame(
  event_time = pre_est$egt,
  att        = pre_est$att.egt,
  se         = pre_est$se.egt
)

df_pre_est[df_pre_est$event_time < 0, ]

```

#AP
```{r}

fe_ap_ipw <- feols(
  ap ~ post_intro
    | county_name + year,
  data    = df_all,
  weights = ~ ipw2,
  cluster = ~ county_name
)

# 3) View the results
summary(fe_ap_ipw)

```


```{r event-study-qp1-ggplot}
# FIX: ggplot2 replaces base-R plot()/arrows() for QP1 event study
es_qp1 <- aggte(did_qp1, type = "dynamic", na.rm = TRUE)

df_es_qp1 <- tibble(
  event_time = es_qp1$egt,
  att        = es_qp1$att.egt,
  se         = es_qp1$se.egt
) |>
  mutate(ci_low = att - 1.96 * se, ci_high = att + 1.96 * se)

p_es_qp1 <- ggplot(df_es_qp1, aes(x = event_time, y = att)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.15, fill = "steelblue") +
  geom_line(color = "steelblue", linewidth = 0.8) +
  geom_point(color = "steelblue", size = 2) +
  scale_x_continuous(breaks = unique(df_es_qp1$event_time)) +
  labs(
    title = "Event-Study: Yelp Entry → Q1 Payroll",
    x     = "Years Since Yelp Entry",
    y     = "ATT(qp1)"
  ) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))

print(p_es_qp1)
ggsave("es_q1_payroll.pdf", plot = p_es_qp1, width = 6, height = 4)
```


```{r}
options(scipen = 10)   # discourage scientific notation
pdf("es_q1_payroll.pdf", width = 6, height = 4)
plot(df_es_qp1$event_time, df_es_qp1$att,
     type = "b", pch = 16, xaxt = "n",
     xlab = "Years Since Yelp Entry",
     ylab = expression(paste("ATT(", qp1, ")")),
     main = "Event‐Study: Yelp Entry \u2192 Q1 Payroll")
axis(1, at = unique(df_es_qp1$event_time))
arrows(x0 = df_es_qp1$event_time,
       y0 = df_es_qp1$ci_low,
       x1 = df_es_qp1$event_time,
       y1 = df_es_qp1$ci_high,
       angle = 90, code = 3, length = 0.05)
abline(h = 0, lty = 2, col = "gray")
dev.off()

```


```{r}

imp_wt_panel <- make_ipw_treated(agg_imp_pca_covid)

df_imp <- imp_wt_panel %>%
  arrange(county_name, year) %>%
  group_by(county_name) %>%
  mutate(
    d_emp    = emp - lag(emp),
    d_review = as.numeric(avg_log_reviews) - lag(as.numeric(avg_log_reviews))
  ) %>%
  ungroup() %>%
  filter(!is.na(d_emp), !is.na(d_review))

out_mod_imp <- lm(d_emp ~ d_review + PC1 + PC2 + PC3 + PC4,
                  data = df_imp)

# 2c) DR score
df_imp <- df_imp %>%
  mutate(
    mu_hat   = predict(out_mod_imp, newdata = df_imp),
    dr_score = mu_hat + ipw_wt * (d_emp - mu_hat)
  )


# create event‐time
df_imp <- df_imp %>%
  mutate(event_time = year - first_review)

fe_imp_es <- feols(
  dr_score ~ i(event_time, ref = 0)
  | county_name + year,
  data    = df_imp,
  weights = ~ ipw_wt,
  cluster = ~ county_name
)

# plot
iplot(fe_imp_es,
      main = "Continuous DR Weighted ES (Imputed Panel)",
      xlab = "Years since Yelp entry",
      ylab = "ATT(emp)")

```

```{r}
fe_imp_cont <- feols(
  d_emp ~ d_review
    | county_name + year,
  data    = df_imp,
  weights = ~ ipw_wt,
  cluster = ~ county_name
)
summary(fe_imp_cont)

```

```{r}
df_imp <- panels_wt_treated$agg_imp_covid

df_imp <- df_imp %>%
  arrange(county_name, year) %>%
  group_by(county_name) %>%
  mutate(
    d_emp    = emp - lag(emp),                        
    d_review = avg_log_reviews - lag(avg_log_reviews) 
  ) %>%
  ungroup() %>%
  filter(!is.na(d_emp), !is.na(d_review), !is.na(ipw_wt))

fe_imp_diff_wt <- feols( 
  d_emp ~ d_review
    | county_name + year,
  data    = df_imp,
  weights = ~ ipw_wt,
  cluster = ~ county_name
)

summary(fe_imp_diff_wt)

```


```{r}
ps_mod <- glm(
  post_intro ~ PC1 + PC2 + PC3 + PC4 + region_name,
  family = binomial(),
  data   = df
)

p_treated <- mean(df$post_intro, na.rm = TRUE)
p_control <- 1 - p_treated

df <- df %>%
  mutate(
    ps = predict(ps_mod, newdata = df, type = "response"),
    sw = if_else(
      post_intro == 1,
      p_treated / ps,
      p_control / (1 - ps)
    )
  )
df_ps <- df %>%
  filter(
    !is.na(PC1), !is.na(PC2), !is.na(PC3), !is.na(PC4),
    !is.na(region_name), !is.na(post_intro)
  )

ps_mod <- glm(
  post_intro ~ PC1 + PC2 + PC3 + PC4 + region_name,
  family = binomial(),
  data   = df_ps
)

p_treated <- mean(df_ps$post_intro)
p_control <- 1 - p_treated

df_ps <- df_ps %>%
  mutate(
    ps = predict(ps_mod, type = "response"),
    sw = if_else(
      post_intro == 1,
      p_treated / ps,
      p_control / (1 - ps)
    )
  )

```


```{r}
fe_bin_sw <- feols(
  qp1 ~ post_intro
    | county_name + year,
  data    = df,
  weights = ~ sw,
  cluster = ~ county_name
)
summary(fe_bin_sw)

```

```{r}
did_list <- list(
  emp  = did_mod2,     # your employment att_gt  
  est  = did_est,      # establishments
  ap   = did_ap,       # annual payroll
  qp1  = did_qp1       # Q1 payroll
)

agg_summary <- imap_dfr(did_list, function(did_obj, outcome_name) {
  agg <- aggte(did_obj, type = "simple", na.rm = TRUE)
  tibble(
    outcome = outcome_name,
    ATT     = agg$overall.att,
    SE      = agg$overall.se,
    CI_lo   = agg$overall.att - 1.96 * agg$overall.se,
    CI_hi   = agg$overall.att + 1.96 * agg$overall.se
  )
})

# 3) inspect
print(agg_summary)

```

```{r}
write.table(
  agg_summary,
  file      = "aggregate_ATT_by_outcome.txt",
  sep       = "\t",
  row.names = FALSE,
  quote     = FALSE
)

res_tex <- kable(
  agg_summary,
  format   = "latex",
  booktabs = TRUE,
  caption  = "Aggregate ATT by Outcome"
)
cat(res_tex, file = "aggregate_ATT_by_outcome.tex")

```


```{r}
baseline_year <- agg_trim_pca_covid %>% 
  pull(year) %>% 
  min(na.rm = TRUE)

bal_df <- agg_trim_pca_covid %>%
  mutate(
    ever_treated = !is.na(first_review),
    pre_year     = if_else(ever_treated, first_review - 1L, baseline_year),
    is_pre       = (year == pre_year)
  ) %>%
  filter(is_pre)

bal_table <- bal_df %>%
  group_by(ever_treated) %>%
  summarise(
    across(
      c(PC1, PC2, PC3, PC4, avg_income_real, avg_age, pct_employed),
      list(mean = ~ mean(.x, na.rm=TRUE),
           sd   = ~ sd(  .x, na.rm=TRUE)),
      .names = "{col}_{fn}"
    ),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols        = -ever_treated,
    names_to    = c("variable", "stat"),
    names_pattern = "(.*)_(mean|sd)$"
  ) %>%
  pivot_wider(
    names_from  = stat,
    values_from = value
  ) %>%
  mutate(
    Group = if_else(ever_treated, "Ever-treated", "Never-treated")
  ) %>%
  select(Group, variable, mean, sd)

# Markdown preview
bal_table %>%
  arrange(variable, Group) %>%
  kable(format = "markdown")

res_tex <- bal_table %>%
  arrange(variable, Group) %>%
  kable(
    format   = "latex",
    booktabs = TRUE,
    caption  = "Baseline Balance on PCs & Covariates"
  )

# 2) Write it out
cat(
  res_tex,
  file = "baseline_balance.tex",
  sep  = "\n"
)

```

```{r}
baseline_year <- agg_trim_pca_covid %>% 
  pull(year) %>% 
  min(na.rm = TRUE)

bal_df <- agg_trim_pca_covid %>%
  mutate(
    ever_treated = !is.na(first_review),
    pre_year     = if_else(ever_treated, first_review - 1L, baseline_year),
    is_pre       = (year == pre_year)
  ) %>%
  filter(is_pre)

bal_table <- bal_df %>%
  group_by(ever_treated) %>%
  summarise(
    across(
      c(PC1, PC2, PC3, PC4, avg_income_real, avg_age, pct_employed),
      list(mean = ~ mean(.x, na.rm=TRUE),
           sd   = ~ sd(  .x, na.rm=TRUE)),
      .names = "{col}_{fn}"
    ),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols        = -ever_treated,
    names_to    = c("variable", "stat"),
    names_pattern = "(.*)_(mean|sd)$"
  ) %>%
  pivot_wider(
    names_from  = stat,
    values_from = value
  ) %>%
  mutate(
    Group = if_else(ever_treated, "Ever-treated", "Never-treated")
  ) %>%
  select(Group, variable, mean, sd)

# Markdown preview
bal_table %>%
  arrange(variable, Group) %>%
  kable(format = "markdown")

# 1) Generate the LaTeX for the balance table
res_tex <- bal_table %>%
  arrange(variable, Group) %>%
  kable(
    format   = "latex",
    booktabs = TRUE,
    caption  = "Baseline Balance on PCs & Covariates"
  )

# 2) Write it out
cat(
  res_tex,
  file = "baseline_balance.tex",
  sep  = "\n"
)

```


```{r}
res_tex <- kable(
  summary_df,
  format   = "latex",
  booktabs = TRUE,
  caption  = "PC1–PC4: Variance Explained and Top Three Loadings"
)
cat(res_tex, file = "pc_summary.tex")

write.table(
  summary_df,
  file       = "pc_summary.csv",
  sep        = ",",
  row.names  = FALSE,
  quote      = FALSE
)

```


```{r}
dr_df <- did_mod2$DIDparams$data

weights <- dr_df$.w

qs <- quantile(weights,
               probs = c(0, 0.01, 0.05, 0.50, 0.95, 0.99, 1),
               na.rm = TRUE)


weight_summary <- tibble(
  Quantile = c("0%", "1%", "5%", "50%", "95%", "99%", "100%"),
  Value    = as.numeric(qs)
)

print(weight_summary)

```


```{r}
latex_weights <- kable(
  weight_summary,
  format   = "latex",
  booktabs = TRUE,
  caption  = "Distribution of DR–DiD Weights (\\.w)"
)

cat(
  latex_weights,
  file = "weight_distribution_table.tex"
)

```

```{r}
cohort_by_county <- 
  agg_trim_pca_covid %>% 
  distinct(county_name, first_review) 


rollout_counts <- 
  cohort_by_county %>% 
  filter(!is.na(first_review)) %>% 
  count(cohort_year = first_review) %>% 
  arrange(cohort_year) 

all_years <- tibble(cohort_year = 2005:2022)

rollout_full <- 
  all_years %>% 
  left_join(rollout_counts, by = "cohort_year") %>% 
  mutate(n = replace_na(n, 0L))

print(rollout_full)

```


```{r}
write_csv(rollout_full, "yelp_rollout_by_year.csv")

rollout_full %>%
  knitr::kable(
    format   = "latex",
    booktabs = TRUE,
    caption  = "Number of U.S. Counties First Getting Yelp Reviews, by Year (2005–2022)"
  ) %>%
  write_lines("yelp_rollout_by_year.tex")

```

```{r}

df_panel <- agg_trim_pca_covid



yearly_review_summary <- df_panel %>%
  filter(num_reviews > 0) %>%           
  group_by(year) %>%                    
  summarize(
    n_counties_with_reviews = n_distinct(county_name),
    avg_of_avg_rating       = mean(avg_rating, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  complete(year = 2005:2022, fill = list(
    n_counties_with_reviews = 0L,
    avg_of_avg_rating       = NA_real_
  )) %>%
  arrange(year)

# 3) Inspect the result
print(yearly_review_summary)

```


```{r}
yearly_review_summary %>%
  kable(
    format   = "latex",
    booktabs = TRUE,
    digits   = c(0, 0, 2),             
    caption  = "Number of Counties with Yelp Reviews and Their Average Rating, by Year"
  ) %>%
  cat(
    file = "yearly_counties_and_avg_rating.tex"
  )

```

```{r}

agg_trim_pca_covid <- agg_trim_pca_covid %>%
  mutate(
    g = as.integer(g), 
    region_name = as.factor(region_name)
  )


treated_only <- agg_trim_pca_covid %>%
  filter(g > 0)


region_cohort_counts <- treated_only %>%
  distinct(county_name, g, region_name) %>%   
  count(region_name, g) %>%                    
  arrange(region_name, g)

print(region_cohort_counts)


region_vs_year_wide <- region_cohort_counts %>%
  tidyr::pivot_wider(
    names_from  = g,
    values_from = n,
    values_fill = 0
  )

print(region_vs_year_wide)


```


```{r}

dr_df <- did_mod2$DIDparams$data
weights <- dr_df$.w
qs <- quantile(weights, probs = c(0, 0.01, 0.05, 0.50, 0.95, 0.99, 1), na.rm = TRUE)
library(tibble)
weight_summary <- tibble(
  Quantile = c("0%", "1%", "5%", "50%", "95%", "99%", "100%"),
  Value    = as.numeric(qs)
)
print(weight_summary)

latex_weights <- kable(
  weight_summary,
  format   = "latex",
  booktabs = TRUE,
  caption  = "Distribution of DR–DiD Weights (\\.w)"
)
cat(latex_weights, file = "weight_distribution_table.tex")

```


```{r}
# 4 Treatment-rollout counts by year

cohort_by_county <- agg_trim_pca_covid %>%
  distinct(county_name, first_review)
rollout_counts <- cohort_by_county %>%
  filter(!is.na(first_review)) %>%
  count(cohort_year = first_review) %>%
  arrange(cohort_year)
all_years <- tibble(cohort_year = 2005:2022)
rollout_full <- all_years %>%
  left_join(rollout_counts, by = "cohort_year") %>%
  mutate(n = replace_na(n, 0L))
print(rollout_full)

write_csv(rollout_full, "yelp_rollout_by_year.csv")
rollout_full %>%
  knitr::kable(
    format   = "latex",
    booktabs = TRUE,
    caption  = "Number of U.S. Counties First Getting Yelp Reviews, by Year (2005–2022)"
  ) %>%
  write_lines("yelp_rollout_by_year.tex")

```



```{r}
# Counties reviews and ratings

df_panel <- agg_trim_pca_covid
yearly_review_summary <- df_panel %>%
  filter(num_reviews > 0) %>%
  group_by(year) %>%
  summarize(
    n_counties_with_reviews = n_distinct(county_name),
    avg_of_avg_rating       = mean(avg_rating, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  complete(year = 2005:2022, fill = list(
    n_counties_with_reviews = 0L,
    avg_of_avg_rating       = NA_real_
  )) %>%
  arrange(year)
print(yearly_review_summary)

yearly_review_summary %>%
  kable(
    format   = "latex",
    booktabs = TRUE,
    digits   = c(0, 0, 2),
    caption  = "Number of Counties with Yelp Reviews and Their Average Rating, by Year"
  ) %>%
  cat(file = "yearly_counties_and_avg_rating.tex")

```


```{r}
# 5 Region to treatment timing

agg_trim_pca_covid <- agg_trim_pca_covid %>%
  mutate(
    g = as.integer(g),
    region_name = as.factor(region_name)
  )
treated_only <- agg_trim_pca_covid %>%
  filter(g > 0)
region_cohort_counts <- treated_only %>%
  distinct(county_name, g, region_name) %>%
  count(region_name, g) %>%
  arrange(region_name, g)
print(region_cohort_counts)

region_vs_year_wide <- region_cohort_counts %>%
  tidyr::pivot_wider(
    names_from  = g,
    values_from = n,
    values_fill = 0
  )
print(region_vs_year_wide)

latex_tab <- kable(
  region_vs_year_wide,
  format      = "latex",
  booktabs    = TRUE,
  caption     = "Count of Counties by Region and First‐Review Year",
  label       = "tab:region_by_year",
  align       = rep("c", ncol(region_vs_year_wide))
)
cat(latex_tab, file = "region_by_year.tex")

```

```{r}
# Means by year

df_panel <- agg_imp_pca_covid
yearly_means <- df_panel %>%
  group_by(year) %>%
  summarise(
    mean_emp = mean(emp, na.rm = TRUE),
    mean_est = mean(est, na.rm = TRUE),
    mean_ap  = mean(ap, na.rm = TRUE),
    mean_qp1 = mean(qp1, na.rm = TRUE)
  ) %>%
  ungroup()
yearly_means

yearly_tex <- kable(
  yearly_means,
  format   = "latex",
  booktabs = TRUE,
  digits   = 0,
  caption  = "County‐Level Mean Outcomes, 2005–2022"
)
cat(yearly_tex, file = "yearly_means.tex")

```

```{r}
# Pre-treatment balance

df_full <- agg_imp_pca_covid
df_pre2005 <- df_full %>%
  mutate(
    first_review = as.integer(first_review),
    ever_treated  = (!is.na(first_review) & first_review > 2005),
    never_treated = is.na(first_review)
  ) %>%
  filter(
    year == 2005,
    is.na(first_review) | first_review > 2005
  ) %>%
  select(county_name, ever_treated, never_treated, PC1, PC2, PC3, PC4, emp, est, ap, qp1)

vars_to_test <- c("PC1","PC2","PC3","PC4","emp","est","ap","qp1")
balance_tbl <- tibble(
  variable   = character(),
  mean_ever  = numeric(),
  mean_never = numeric(),
  t_stat     = numeric(),
  p_value    = numeric()
)
for (v in vars_to_test) {
  tmp <- df_pre2005 %>% select(!!sym(v), ever_treated) %>%
         rename(x = !!sym(v))
  tt  <- t.test(x ~ ever_treated, data = tmp)
  balance_tbl <- bind_rows(balance_tbl, tibble(
    variable   = v,
    mean_ever  = mean(tmp$x[tmp$ever_treated], na.rm = TRUE),
    mean_never = mean(tmp$x[tmp$ever_treated == FALSE], na.rm = TRUE),
    t_stat     = as.numeric(tt$statistic),
    p_value    = tt$p.value
  ))
}
print(balance_tbl)

balance_tex <- kable(
  balance_tbl,
  format   = "latex",
  booktabs = TRUE,
  digits   = c(0, 3, 3, 2, 3),
  caption  = "Pre‐Treatment Balance: 2005 Means (Ever‐Treated vs Never‐Treated)"
)
cat(balance_tex, file = "pre_treatment_balance.tex")

```



```{r}
# One DID per sector

all_sectors <- c("Food", "Health", "Other", "Retail")
all_counties <- agg_imp_pca_covid %>%
  distinct(county_name) %>%
  pull(county_name)
all_years <- sort(unique(agg_imp_pca_covid$year))
full_sector_grid <- expand.grid(
  county_name    = all_counties,
  category_group = all_sectors,
  year           = all_years,
  stringsAsFactors = FALSE
) %>%
  as_tibble()
sect_full <- full_sector_grid %>%
  left_join(
    sect_imp_pca_covid %>%
      select(county_name, category_group, year, num_reviews, avg_log_reviews, avg_rating),
    by = c("county_name", "category_group", "year")
  ) %>%
  mutate(
    num_reviews     = replace_na(num_reviews,    0),
    avg_log_reviews = replace_na(avg_log_reviews, 0),
    avg_rating      = replace_na(avg_rating,     0)
  )
sect_full2 <- sect_full %>%
  left_join(
    agg_imp_pca_covid %>%
      select(county_name, year, PC1, PC2, PC3, PC4, covid_case_pct, covid_death_pct,
             region_name, emp, est, ap, qp1),
    by = c("county_name", "year")
  )
sect_full3 <- sect_full2 %>%
  group_by(county_name, category_group) %>%
  mutate(
    sector_first_review = if_else(
      any(num_reviews > 0),
      min(year[num_reviews > 0]),
      NA_integer_
    )
  ) %>%
  ungroup() %>%
  mutate(
    g        = if_else(is.na(sector_first_review), 0L, sector_first_review),
    unit_key = paste(county_name, category_group, sep = "_"),
    unit_id  = as.integer(factor(unit_key)),
    year_num = as.integer(year)
  ) %>%
  select(
    county_name, category_group, unit_id, year_num, g,
    PC1, PC2, PC3, PC4, region_name,
    num_reviews, avg_log_reviews, avg_rating,
    emp, est, ap, qp1
  )
sect_full3 %>%
  group_by(category_group) %>%
  summarize(
    total_counties_here = n_distinct(unit_id),
    n_ever_treated      = n_distinct(unit_id[g > 0]),
    n_never_treated     = n_distinct(unit_id[g == 0])
  )

```{r sector-did-loop}
# FIX: replaced four near-identical sector_dids/sector_dids1/sector_dids2/sector_dids3
# blocks with a single loop over outcomes. Results stored in a named list.
# Access: sector_dids_all[["emp"]][["Food"]]

outcomes <- c("emp", "est", "ap", "qp1")

set.seed(42)
sector_dids_all <- map(outcomes, function(yvar) {
  purrr::imap(
    split(sect_full3, sect_full3$category_group),
    ~ {
      message("  → att_gt(): outcome = ", yvar, "  sector = ", .y)
      att_gt(
        yname         = yvar,
        tname         = "year_num",
        idname        = "unit_id",
        gname         = "g",
        xformla       = ~ PC1 + PC2 + PC3 + PC4 + region_name,
        data          = .x,
        control_group = "notyettreated",
        est_method    = "dr",
        bstrap        = TRUE,
        biters        = 200,
        cband         = FALSE
      )
    }
  )
}) |> set_names(outcomes)

# Aggregate ATT per outcome per sector and export LaTeX tables
outcome_labels <- c(
  emp  = "Employment",
  est  = "Establishments",
  ap   = "Annual Payroll",
  qp1  = "1st Quarter Payroll"
)

walk(outcomes, function(yvar) {
  agg_df <- purrr::imap_dfr(
    sector_dids_all[[yvar]],
    function(did_obj, sector_name) {
      overall <- aggte(did_obj, type = "simple", na.rm = TRUE)
      tibble(
        sector = sector_name,
        ATT    = overall$overall.att,
        SE     = overall$overall.se,
        CI_lo  = overall$overall.att - 1.96 * overall$overall.se,
        CI_hi  = overall$overall.att + 1.96 * overall$overall.se
      )
    }
  ) |> as.data.frame()

  print(agg_df)

  tex <- kable(
    agg_df,
    format   = "latex",
    booktabs = TRUE,
    caption  = paste0(
      "Doubly-Robust Staggered DiD: Aggregate ATT for ",
      outcome_labels[[yvar]], ", by Yelp Category"
    )
  )
  writeLines(tex, paste0("sector_ATT_", yvar, ".tex"))
})
```























