---
title: "Dose-Response: Does More Review Growth Mean a Bigger Effect?"
author: "Manolis Giannitselis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
```

```{r example-data, echo=FALSE}
# Small simulated stand-in for the real panel, so this file runs
# standalone. ipw_wt comes from the same weighting function used in
# robustness-checks/.
set.seed(42)
n_counties <- 60
years <- 2015:2023

df <- expand.grid(county_id = 1:n_counties, year = years) %>%
  arrange(county_id, year) %>%
  group_by(county_id) %>%
  mutate(
    PC1 = rnorm(n()), PC2 = rnorm(n()), PC3 = rnorm(n()), PC4 = rnorm(n()),
    avg_log_reviews = rnorm(n(), 2, 1) + 0.1 * (year - min(years)),
    d_review = avg_log_reviews - lag(avg_log_reviews),
    emp   = 500 + 3 * (year - min(years)) + 8 * pmax(d_review, 0) + rnorm(n(), 0, 5),
    d_emp = emp - lag(emp)
  ) %>%
  ungroup() %>%
  filter(!is.na(d_review), !is.na(d_emp))

make_ipw_treated <- function(data){
  mu0 <- mean(data$d_review); sigma0 <- sd(data$d_review)
  cond_mod  <- lm(d_review ~ PC1 + PC2 + PC3 + PC4, data = data)
  mu_hat    <- predict(cond_mod, data)
  sigma_hat <- sd(residuals(cond_mod))
  data %>%
    mutate(
      log_wt   = dnorm(d_review, mu0, sigma0, log = TRUE) -
                 dnorm(d_review, mu_hat, sigma_hat, log = TRUE),
      log_wt_c = log_wt - median(log_wt, na.rm = TRUE),
      ipw_wt   = exp(log_wt_c),
      ipw_wt   = ipw_wt / mean(ipw_wt, na.rm = TRUE)
    )
}

df <- make_ipw_treated(df)
```

## Step 1: Model the expected change in employment

```{r outcome-model}
# Predicts d_emp from the change in reviews and the same PCA controls
# used throughout the project.
outcome_mod <- lm(d_emp ~ d_review + PC1 + PC2 + PC3 + PC4, data = df)
summary(outcome_mod)
```

## Step 2: Combine into a doubly-robust score

```{r dr-score}
df <- df %>%
  mutate(
    mu_hat_emp = predict(outcome_mod, newdata = df),
    dr_score   = mu_hat_emp + ipw_wt * (d_emp - mu_hat_emp)
  )

hist(df$dr_score, breaks = 30, main = "DR Scores", xlab = "dr_score")
```

`dr_score` combines the outcome model's prediction with an
IPW-weighted correction term — the same doubly-robust logic behind the
main DiD specification (see [`did-analysis/`](../did-analysis/)), but
applied here directly to a continuous measure of review growth rather
than a binary treatment indicator.

## Step 3: Bin by review growth and look for a dose-response pattern

```{r binned-dose-response}
df_bins <- df %>%
  mutate(bin = ntile(d_review, 4), mid = ave(d_review, bin, FUN = mean))

dose_resp <- df_bins %>%
  group_by(bin, mid) %>%
  summarise(
    avg_dr = mean(dr_score, na.rm = TRUE),
    sd_dr  = sd(dr_score, na.rm = TRUE),
    n_obs  = n(),
    se_dr  = sd_dr / sqrt(n_obs),
    ci_lo  = avg_dr - 1.96 * se_dr,
    ci_hi  = avg_dr + 1.96 * se_dr,
    .groups = "drop"
  )

dose_resp
```

```{r dose-response-plot}
with(dose_resp, {
  plot(mid, avg_dr, ylim = range(ci_lo, ci_hi),
       pch = 16, xlab = "Change in avg_log_reviews (bin midpoint)",
       ylab = "Average DR Score (change in employment)",
       main = "Dose-Response with 95% CI")
  arrows(mid, ci_lo, mid, ci_hi, angle = 90, code = 3, length = 0.05)
})
```

## Why this check matters

The main DiD result answers a yes/no question: did crossing the review
threshold change local business activity? It doesn't say whether a
*bigger* increase in reviews produces a *bigger* effect, or whether the
effect is flat once any meaningful increase happens. Binning
counties by how much their review activity actually grew, and plotting
the average doubly-robust score in each bin, is a way of checking for
that dose-response pattern directly — a genuine causal relationship
would generally be expected to show *some* upward pattern across bins,
rather than a flat line or something non-monotonic.

This isn't a formal robustness check in the same sense as the ones in
[`robustness-checks/`](../robustness-checks/) — it's closer to
probing whether the binary treatment story in `did-analysis/` is
hiding a richer relationship underneath, rather than confirming or
rejecting the main estimate directly.
